---
title: "Comparing fod web model results from different sites"
author: "Connor Shea"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: 
  #html_document: 
  bookdown::html_document2:  
    self-contained: yes
    theme: cerulean #paper #cosmo #journal #readable
    toc: true
    smooth_scroll: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    fig_caption: yes
    code_folding: hide
bibliography: Utilities/MesoPelaZooAA.bib
csl: Utilities/LnO.csl
link-citations: yes
---

```{r setup, echo=FALSE, warning=FALSE}
## This chunk sets up a working directory, loads packages, defines a couple functions, and sets global chunk options for the .Rmd document

# clean up
rm(list=ls()) 

# fresh start? If FALSE (select 2 in hard bracket), will only rerun a chunk if
# changes are detected within the text of that chunk.
rmCache <- c(TRUE, FALSE)[2] 
tfn <- knitr::current_input()              # name of this file
tfn <- substr(tfn, 1, nchar(tfn)-4)        # Remove the ".Rmd"
tfn_cache <- paste0("Caches/", tfn, "_cache")         # Append "_cache" to it
tfn_figures <- paste0("Figures/", tfn, "_figures")         # Append "_figures" to it
if (rmCache) {
  if (file.exists(tfn_cache))                # If the cache exists...
    unlink(tfn_cache, recursive=TRUE)        # ...delete it.
}

## load packages quietly
shhh <- suppressPackageStartupMessages # It's a library, so shhh!
want <- c("knitr", 
          "readxl", # for reading xl files
          "MASS", # some statistics including lda
          "vegan", # ecology statistics
          "FactoMineR", # includes PCA function and utilities
          "factoextra", # extra utilities for FactoMineR
          "runjags", # To run Bayesian models
          "TruncatedDistributions", # To generate truncate porbability distributions
          "coda",  
          "DT", # makes nice sortable tables
          "openxlsx", # writes to .xlsx files
          "compositions", 
          "kableExtra",
          "zeallot", 
          "magrittr", 
          "DirichletReg", 
          "Ternary", 
          "png",
          "ggplot2",
          "ggpubr",
          "ggstance", # for vertical position dodging
          "ggtern", # for ternary plots in ggplot2
          "ggforce", # for specific extra plotting capabilities (facet_row())
          "plotly",
          "gridExtra",
          "graphics",
          "reshape2",
          "dplyr",
          "effects",
          "ggrepel",
          "scales"
          )
for (pkg in want) shhh(library(pkg, character.only=TRUE))

# set some chunk options
gr <- (1+sqrt(5))/2 # golden ratio, for figures
opts_chunk$set(comment="  ",
               # fig.asp=0.9/gr,       # <--- gr used here
               fig.align="center",
               # fig.width=5,
               out.width="95%",
               dpi=96, # set to 300 for important figures
               dev="png", # png, svg, pdf, jpg, tiff
               #echo=FALSE,
               cache=c(TRUE, FALSE)[2], 
               cache.path = paste0(tfn_cache,"/"),
               fig.path = paste0(tfn_figures,"/"),
               eval.after="fig.cap", # for dynamic captions
               collapse=TRUE
               )

## a couple of lines we need to run every time we knit
# setting the ggplot theme
theme_set(theme_classic2()+
            theme(panel.grid.major.x = element_line(colour = "grey95"),
                  panel.grid.major.y = element_line(colour = "grey95")))
# defining a ggplot object to remove the x axis
no.x.axis <- theme(axis.title.x=element_blank(),
                   axis.text.x=element_blank(),
                   axis.ticks.x=element_blank())
# defining a ggplot object to remove the y axis
no.y.axis <- theme(axis.title.y=element_blank(),
                   axis.text.y=element_blank(),
                   axis.ticks.y=element_blank())

source("Functions/calcSDs.R")         # SDmean() and SDsum()
source("Functions/Post_Mode.R")       # post.mode()
```  

<!-- The following commands provide a shorthand for common symbols when used in math mode. -->

\newcommand{\um}{\ \mu \mathrm{ m}}
\newcommand{\mm}{\mathrm{\ mm}}
\newcommand{\m}{\mathrm{\ m}}
\newcommand{\N}{\mathrm{^{15}\text{N}}}
\newcommand{\dN}{\mathrm{\delta^{15}\text{N}}}
\newcommand{\dNAA}{\mathrm{\delta^{15}\text{N}_\text{AA}}}
\newcommand{\dNSAA}{\mathrm{\delta^{15}\text{N}_\text{SAA}}}
\newcommand{\dNTAA}{\mathrm{\delta^{15}\text{N}_\text{TAA}}}
\newcommand{\dNtr}{\mathrm{\delta^{15}\text{N}_\text{tr}}}
\newcommand{\dNsrc}{\mathrm{\delta^{15}\text{N}_\text{src}}}
\newcommand{\dNphe}{\mathrm{\delta^{15}N_{phe}}}
\newcommand{\dNthr}{\mathrm{\delta^{15}N_{thr}}}
\newcommand{\dNala}{\mathrm{\delta^{15}N_{ala}}}
\newcommand{\dNglx}{\mathrm{\delta^{15}N_{glx}}}
\newcommand{\dNThrPhe}{\mathrm{\delta^{15}N_{thr-phe}}}
\newcommand{\dNAlaPhe}{\mathrm{\delta^{15}N_{ala-phe}}}
\newcommand{\dNglxphe}{\mathrm{\delta^{15}N_{glx-phe}}}
\newcommand{\DN}{\mathrm{\Delta^{15}\text{N}}}
\newcommand{\DNAA}{\mathrm{\Delta^{15}\text{N}_\text{AA}}}
\newcommand{\C}{\mathrm{^{13}\text{C}}}
\newcommand{\dC}{\mathrm{\delta^{13}\text{C}}}
\newcommand{\dCAA}{\mathrm{\delta^{13}\text{C}_\text{AA}}}
\newcommand{\dCEAA}{\mathrm{\delta^{13}\text{C}_\text{EAA}}}
\newcommand{\dCNAA}{\mathrm{\delta^{13}\text{C}_\text{NAA}}}
\newcommand{\permil}{‰}
\newcommand{\degree}{°}
\newcommand{\TP}{\mathrm{TP}}
\newcommand{\TPala}{\mathrm{TP_{ala-phe}}}
\newcommand{\TPglx}{\mathrm{TP_{glx-phe}}}
\newcommand{\TPts}{\mathrm{TP_{tr-src}}}
\newcommand{\dTP}{\mathrm{\Delta TP_{ala-glx}}}

# Summary {-}  

Here we will be comparing the model results from all locations across the North Pacific. We will want to produce the following comparison plots.

    - Δ15N vaues at all sites
    - TP of 1-2 mm zooplankton at all sites
    - Mixing coefficients for 1-2 mm zooplankton st all sites
    - SAA vs depth plots at all sites
    
First we need to import the data from prior model runs.

```{r load-data, cache=TRUE}
path <- dirname(rstudioapi::getActiveDocumentContext()$path)

load(paste(path,"/Data/OMSM_posteriors_OSP.RData",sep=""))
posts.OSP <- posts
posts.long.OSP <- posts.long
data.all.OSP <- Data.all
# data.parts.OSP <- data.avg.parts
# data.parts.OSP$Location <- "OSP"
load(paste(path,"/Data/OMSM_posteriors_ALOHA-Summer.RData",sep=""))
posts.ALOHAS <- posts
posts.long.ALOHAS <- posts.long
data.all.ALOHAS <- subset(Data.all, Location == "ALOHA S")
# data.parts.ALOHAS <- data.avg.parts
# data.parts.ALOHAS$Location <- "ALOHA S"
load(paste(path,"/Data/OMSM_posteriors_ALOHA-Winter.RData",sep=""))
posts.ALOHAW <- posts
posts.long.ALOHAW <- posts.long
data.all.ALOHAW <- subset(Data.all, Location == "ALOHA W")
# data.parts.ALOHAW <- data.avg.parts
# data.parts.ALOHAW$Location <- "ALOHA W"
load(paste(path,"/Data/OMSM_posteriors_8N.RData",sep=""))
posts.8N <- posts
posts.long.8N <- posts.long
data.all.8N <- Data.all
# data.parts.8N <- data.avg.parts
# data.parts.8N$Location <- "8 N"
load(paste(path,"/Data/OMSM_posteriors_5N.RData",sep=""))
posts.5N <- posts
posts.long.5N <- posts.long
data.all.5N <- Data.all
# data.parts.5N <- data.avg.parts
# data.parts.5N$Location <- "5 N"
load(paste(path,"/Data/OMSM_posteriors_PAP.RData",sep=""))
posts.PAP <- posts
posts.long.PAP <- posts.long
data.all.PAP <- Data.all
# data.parts.5N <- data.avg.parts
# data.parts.5N$Location <- "5 N"

data.all <- 
  rbind(
    data.all.5N,
    data.all.8N,
    data.all.ALOHAS,
    data.all.ALOHAW,
    data.all.OSP,
    data.all.PAP
  )



# There are also some vectors we need to define
# Indicate the name of the column describing the organic matter source to which
# each sample belongs
# Source_Variable <- "Source"
# Indicate the names representing each possible source of organic matter in the
# order in which you would like the referenced
Sources <- c("Surface","Large","Small")

# List the name of any additional variables that should be stored for analysis
Additional_variables <- c("Location","Epoch","Event","Size","Depth","Type")

# variables <- c(Source_Variable, Additional_variables)
variables <- c(Additional_variables)


```

# Mixing Coefficient Depth Profiles {-}

First we'll try and make a full page figure of all model results from all locations.

```{r f_depth_profiles, DPI = 300, fig.width=8.5, fig.height=10, cache=FALSE}
# for (i in c("5 N","8 N","ALOHA S","ALOHA W","OSP")) {
# Making master data frames including all locations
# Also putting those into long format for plotting
sizes <- c("0.06-0.2 mm", "0.2-0.5 mm", "1-2 mm", "2-5 mm", ">5 mm",
           "Oithonid", "Harpactacoid", "Pleuromamma", "Peuromamma", "Ostracod", "Oncaeid", "Gaussia", "Chaetognath","Radiolarian", "Metridia", "Neocalanus","Gaetanus")
f.mode <-
  subset(
  bind_rows(
    posts.5N$f$mode[c(variables,"Surface","Large","Small")],
    posts.8N$f$mode[c(variables,"Surface","Large","Small")],
    posts.ALOHAS$f$mode[c(variables,"Surface","Large","Small")],
    posts.ALOHAW$f$mode[c(variables,"Surface","Large","Small")],
    posts.OSP$f$mode[c(variables,"Surface","Large","Small")],
    posts.PAP$f$mode[c(variables,"Surface","Large","Small")]),
  Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")# & Location == i)
f.mode.long <-
  melt(f.mode,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.mode.long$Size <- factor(f.mode.long$Size, levels = sizes)
f.HDI95 <-
  subset(
    bind_rows(
    posts.5N$f$HDI95[c(variables,"Surface","Large","Small")],
    posts.8N$f$HDI95[c(variables,"Surface","Large","Small")],
    posts.ALOHAS$f$HDI95[c(variables,"Surface","Large","Small")],
    posts.ALOHAW$f$HDI95[c(variables,"Surface","Large","Small")],
    posts.OSP$f$HDI95[c(variables,"Surface","Large","Small")],
    posts.PAP$f$HDI95[c(variables,"Surface","Large","Small")]),
  Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")# & Location == i)
f.HDI95.long <-
  melt(f.HDI95,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.HDI95.long$Size <- factor(f.HDI95.long$Size, levels = sizes)
f.HDI90 <-
  subset(
    bind_rows(
    posts.5N$f$HDI90[c(variables,"Surface","Large","Small")],
    posts.8N$f$HDI90[c(variables,"Surface","Large","Small")],
    posts.ALOHAS$f$HDI90[c(variables,"Surface","Large","Small")],
    posts.ALOHAW$f$HDI90[c(variables,"Surface","Large","Small")],
    posts.OSP$f$HDI90[c(variables,"Surface","Large","Small")],
    posts.PAP$f$HDI90[c(variables,"Surface","Large","Small")]),
  Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")# & Location == i)
f.HDI90.long <-
  melt(f.HDI90,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.HDI90.long$Size <- factor(f.HDI90.long$Size, levels = sizes)
f.HDI75 <-
  subset(
    bind_rows(
    posts.5N$f$HDI75[c(variables,"Surface","Large","Small")],
    posts.8N$f$HDI75[c(variables,"Surface","Large","Small")],
    posts.ALOHAS$f$HDI75[c(variables,"Surface","Large","Small")],
    posts.ALOHAW$f$HDI75[c(variables,"Surface","Large","Small")],
    posts.OSP$f$HDI75[c(variables,"Surface","Large","Small")],
    posts.PAP$f$HDI75[c(variables,"Surface","Large","Small")]),
  Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")# & Location == i)
f.HDI75.long <-
  melt(f.HDI75,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.HDI75.long$Size <- factor(f.HDI75.long$Size, levels = sizes)
f.HDI50 <-
  subset(
    bind_rows(
    posts.5N$f$HDI50[c(variables,"Surface","Large","Small")],
    posts.8N$f$HDI50[c(variables,"Surface","Large","Small")],
    posts.ALOHAS$f$HDI50[c(variables,"Surface","Large","Small")],
    posts.ALOHAW$f$HDI50[c(variables,"Surface","Large","Small")],
    posts.OSP$f$HDI50[c(variables,"Surface","Large","Small")],
    posts.PAP$f$HDI50[c(variables,"Surface","Large","Small")]),
  Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")# & Location == i)
f.HDI50.long <-
  melt(f.HDI50,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.HDI50.long$Size <- factor(f.HDI50.long$Size, levels = sizes)

# Appending columns with the min and max of the 95% HDI to the mode data frame.
f.mode.long$min95 <- f.HDI95.long$f[seq(1,nrow(f.HDI95.long),2)]
f.mode.long$max95 <- f.HDI95.long$f[seq(2,nrow(f.HDI95.long),2)]

# # print(
# ggplot()+
#   # geom_path(
#   #   data=f.mode.long,
#   #   aes(x=f, y=Depth, color = Size, group = interaction(Size)),
#   #   size = 1, alpha = 1,
#   #   position = position_dodgev(height = 100))+
#   geom_line(
#     data = f.HDI95.long,
#     aes(x = f, y = Depth, color = Size, group = interaction(Depth, Size)),
#     alpha = 0.5, size = 1,
#     position = position_dodgev(height = 100))+
#   geom_line(
#     data = f.HDI90.long,
#     aes(x = f, y = Depth, color = Size, group = interaction(Depth, Size)),
#     alpha = 0.7, size = 1.5,
#     position = position_dodgev(height = 100))+
#   geom_line(
#     data = f.HDI75.long,
#     aes(x = f, y = Depth, color = Size, group = interaction(Depth, Size)),
#     alpha = 1, size = 2,
#     position = position_dodgev(height = 100))+
#   geom_line(
#     data = f.HDI50.long,
#     aes(x = f, y = Depth, color = Size, group = interaction(Depth, Size)),
#     alpha = 1, size = 3,
#     position = position_dodgev(height = 100))+
#   geom_point(
#     data=f.mode.long,
#     aes(x=f, y=Depth, fill = Size, group = interaction(Depth, Size)),
#     size = 2.5, shape = 22,
#     position = position_dodgev(height = 100))+
#   labs()+
#   facet_grid(cols = vars(Source),
#              rows = vars(factor(Location, levels = c("PAP","OSP","ALOHA S","ALOHA W","8 N","5 N"))),
#              scales = "free_y")+
#   # facet_wrap(~ Source, nrow = 1)+
#   scale_y_reverse(breaks = c(0,250,500,750,1000,1250,1500), minor_breaks = c())+
#   coord_cartesian(ylim=c(NA,0))+
#   theme_light()#+
#   # ggtitle(i)
# # )
# # }


f_depth_plots <- function(
    posts
){
  f.mode <- 
  subset(
    posts$f$mode[c(variables,"Surface","Large","Small")],
  Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")# & Location == i)
f.mode.long <-
  melt(f.mode,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.mode.long$Size <- factor(f.mode.long$Size, levels = sizes)
f.HDI95 <- 
  subset(
    posts$f$HDI95[c(variables,"Surface","Large","Small")],
  Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")# & Location == i)
f.HDI95.long <-
  melt(f.HDI95,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.HDI95.long$Size <- factor(f.HDI95.long$Size, levels = sizes)
f.HDI90 <- 
  subset(
    posts$f$HDI90[c(variables,"Surface","Large","Small")],
  Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")# & Location == i)
f.HDI90.long <-
  melt(f.HDI90,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.HDI90.long$Size <- factor(f.HDI90.long$Size, levels = sizes)
f.HDI75 <- 
  subset(
    posts$f$HDI75[c(variables,"Surface","Large","Small")],
  Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")# & Location == i)
f.HDI75.long <-
  melt(f.HDI75,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.HDI75.long$Size <- factor(f.HDI75.long$Size, levels = sizes)
f.HDI50 <- 
  subset(
    posts$f$HDI50[c(variables,"Surface","Large","Small")],
  Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")# & Location == i)
f.HDI50.long <-
  melt(f.HDI50,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.HDI50.long$Size <- factor(f.HDI50.long$Size, levels = sizes)

# Appending columns with the min and max of the 95% HDI to the mode data frame.
f.mode.long$min95 <- f.HDI95.long$f[seq(1,nrow(f.HDI95.long),2)]
f.mode.long$max95 <- f.HDI95.long$f[seq(2,nrow(f.HDI95.long),2)]

sizes <- c("0.2-0.5 mm", "1-2 mm", "2-5 mm", ">5 mm")

# print(
ggplot()+
  # geom_path(
  #   data=f.mode.long,
  #   aes(x=f, y=Depth, color = Size, group = interaction(Size)),
  #   size = 1, alpha = 1,
  #   position = position_dodgev(height = 100))+
  geom_line(
    data = f.HDI95.long,
    aes(x = f, y = Depth, color = Size, group = interaction(Depth, Size)),
    alpha = 0.5, size = 1,
    position = position_dodgev(height = 100))+
  geom_line(
    data = f.HDI90.long,
    aes(x = f, y = Depth, color = Size, group = interaction(Depth, Size)),
    alpha = 0.7, size = 1.5,
    position = position_dodgev(height = 100))+
  geom_line(
    data = f.HDI75.long,
    aes(x = f, y = Depth, color = Size, group = interaction(Depth, Size)),
    alpha = 1, size = 2,
    position = position_dodgev(height = 100))+
  geom_line(
    data = f.HDI50.long,
    aes(x = f, y = Depth, color = Size, group = interaction(Depth, Size)),
    alpha = 1, size = 3,
    position = position_dodgev(height = 100))+
  geom_point(
    data=f.mode.long,
    aes(x=f, y=Depth, fill = Size, group = interaction(Depth, Size)),
    size = 2.5, shape = 22,
    position = position_dodgev(height = 100))+
  labs()+
  facet_wrap(~ Source)+
  # facet_wrap(~ Source, nrow = 1)+
  scale_y_reverse(breaks = c(0,250,500,750,1000,1250,1500), minor_breaks = c())+
  scale_x_continuous(breaks = c(0,0.5,1), labels = c("0","0.5","1"))+
  coord_cartesian(ylim=c(NA,-50), expand = FALSE)+
  scale_color_manual(breaks = sizes,
                     values = hue_pal()(length(sizes)))+
  scale_fill_manual(breaks = sizes,
                     values = hue_pal()(length(sizes)))+
  theme_light()+theme(strip.text.x = element_text(size = 8),
                        axis.title.x = element_blank(),
                        axis.title.y = element_blank(),
                        plot.title = element_text(size=12, hjust=0.5))
}

plot.PAP <-
  f_depth_plots(posts.PAP) + ggtitle("North Atlantic")+
  coord_cartesian(ylim=c(1000,-50), expand = FALSE)
plot.OSP <-
  f_depth_plots(posts.OSP) + ggtitle("Station Papa")+
  coord_cartesian(ylim=c(1000,-50), expand = FALSE)
plot.ALOHAS <-
  f_depth_plots(posts.ALOHAS) + ggtitle("ALOHA Summer")
plot.ALOHAW <-
  f_depth_plots(posts.ALOHAW) + ggtitle("ALOHA Winter")
plot.8N <-
  f_depth_plots(posts.8N) + ggtitle("8° N")
plot.5N <-
  f_depth_plots(posts.5N) + ggtitle("5° N")

plot.blank <-
  ggplot+geom_blank()+theme_bw()+theme(panel.border=element_blank())

ggarrange(
  ggplot() + geom_blank() + ylab("Depth (m)"),

ggarrange(plot.OSP,    plot.PAP,
          plot.ALOHAS, plot.ALOHAW,
          plot.5N,     plot.8N,
          ncol = 2, nrow=3,
          common.legend = TRUE, legend="top"),
  
  ggplot() + geom_blank() + theme_void(),
  ggplot() + geom_blank() + xlab("Mixing Coefficients"),
  widths = c(0.03,1),
  heights = c(1,0.05)
)


```

```{r f_depth_profiles_taxa, DPI = 300, fig.width=8.5, fig.height=6, cache=FALSE}
# for (i in c("5 N","8 N","ALOHA S","ALOHA W","OSP")) {
# Making master data frames including all locations
# Also putting those into long format for plotting
sizes <- c("0.06-0.2 mm", "0.2-0.5 mm", "1-2 mm", "2-5 mm", ">5 mm",
           "Oithonid", "Harpactacoid", "Pleuromamma", "Peuromamma", "Ostracod", "Oncaeid", "Gaussia", "Chaetognath","Radiolarian", "Metridia", "Neocalanus","Gaetanus")
f.mode <-
  subset(
  bind_rows(
    posts.5N$f$mode[c(variables,"Surface","Large","Small")],
    posts.8N$f$mode[c(variables,"Surface","Large","Small")],
    posts.ALOHAS$f$mode[c(variables,"Surface","Large","Small")],
    posts.ALOHAW$f$mode[c(variables,"Surface","Large","Small")],
    posts.OSP$f$mode[c(variables,"Surface","Large","Small")],
    posts.PAP$f$mode[c(variables,"Surface","Large","Small")]),
  Size != "0.06-0.2 mm" & Size != "0.2-0.5 mm" & Size != "1-2 mm" & Size != "2-5 mm" & Size != ">5 mm")# & Location == i)
f.mode.long <-
  melt(f.mode,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.mode.long$Size <- factor(f.mode.long$Size, levels = sizes)
f.HDI95 <-
  subset(
    bind_rows(
    posts.5N$f$HDI95[c(variables,"Surface","Large","Small")],
    posts.8N$f$HDI95[c(variables,"Surface","Large","Small")],
    posts.ALOHAS$f$HDI95[c(variables,"Surface","Large","Small")],
    posts.ALOHAW$f$HDI95[c(variables,"Surface","Large","Small")],
    posts.OSP$f$HDI95[c(variables,"Surface","Large","Small")],
    posts.PAP$f$HDI95[c(variables,"Surface","Large","Small")]),
  Size != "0.06-0.2 mm" & Size != "0.2-0.5 mm" & Size != "1-2 mm" & Size != "2-5 mm" & Size != ">5 mm")# & Location == i)
f.HDI95.long <-
  melt(f.HDI95,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.HDI95.long$Size <- factor(f.HDI95.long$Size, levels = sizes)
f.HDI90 <-
  subset(
    bind_rows(
    posts.5N$f$HDI90[c(variables,"Surface","Large","Small")],
    posts.8N$f$HDI90[c(variables,"Surface","Large","Small")],
    posts.ALOHAS$f$HDI90[c(variables,"Surface","Large","Small")],
    posts.ALOHAW$f$HDI90[c(variables,"Surface","Large","Small")],
    posts.OSP$f$HDI90[c(variables,"Surface","Large","Small")],
    posts.PAP$f$HDI90[c(variables,"Surface","Large","Small")]),
  Size != "0.06-0.2 mm" & Size != "0.2-0.5 mm" & Size != "1-2 mm" & Size != "2-5 mm" & Size != ">5 mm")# & Location == i)
f.HDI90.long <-
  melt(f.HDI90,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.HDI90.long$Size <- factor(f.HDI90.long$Size, levels = sizes)
f.HDI75 <-
  subset(
    bind_rows(
    posts.5N$f$HDI75[c(variables,"Surface","Large","Small")],
    posts.8N$f$HDI75[c(variables,"Surface","Large","Small")],
    posts.ALOHAS$f$HDI75[c(variables,"Surface","Large","Small")],
    posts.ALOHAW$f$HDI75[c(variables,"Surface","Large","Small")],
    posts.OSP$f$HDI75[c(variables,"Surface","Large","Small")],
    posts.PAP$f$HDI75[c(variables,"Surface","Large","Small")]),
  Size != "0.06-0.2 mm" & Size != "0.2-0.5 mm" & Size != "1-2 mm" & Size != "2-5 mm" & Size != ">5 mm")# & Location == i)
f.HDI75.long <-
  melt(f.HDI75,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.HDI75.long$Size <- factor(f.HDI75.long$Size, levels = sizes)
f.HDI50 <-
  subset(
    bind_rows(
    posts.5N$f$HDI50[c(variables,"Surface","Large","Small")],
    posts.8N$f$HDI50[c(variables,"Surface","Large","Small")],
    posts.ALOHAS$f$HDI50[c(variables,"Surface","Large","Small")],
    posts.ALOHAW$f$HDI50[c(variables,"Surface","Large","Small")],
    posts.OSP$f$HDI50[c(variables,"Surface","Large","Small")],
    posts.PAP$f$HDI50[c(variables,"Surface","Large","Small")]),
  Size != "0.06-0.2 mm" & Size != "0.2-0.5 mm" & Size != "1-2 mm" & Size != "2-5 mm" & Size != ">5 mm")# & Location == i)
f.HDI50.long <-
  melt(f.HDI50,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.HDI50.long$Size <- factor(f.HDI50.long$Size, levels = sizes)

# Appending columns with the min and max of the 95% HDI to the mode data frame.
f.mode.long$min95 <- f.HDI95.long$f[seq(1,nrow(f.HDI95.long),2)]
f.mode.long$max95 <- f.HDI95.long$f[seq(2,nrow(f.HDI95.long),2)]

sizes <- c("Oithonid", "Harpactacoid", "Pleuromamma", "Peuromamma", "Ostracod", "Oncaeid", "Gaussia", "Chaetognath","Radiolarian", "Metridia", "Neocalanus","Gaetanus")

f_depth_plots <- function(
    posts
){
  f.mode <-
  subset(
    posts$f$mode[c(variables,"Surface","Large","Small")],
  Size != "0.2-0.5 mm" & Size != "1-2 mm" & Size != "2-5 mm" & Size != ">5 mm")# & Location != i)
f.mode.long <-
  melt(f.mode,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.mode.long$Size <- factor(f.mode.long$Size, levels = sizes)
f.HDI95 <-
  subset(
    posts$f$HDI95[c(variables,"Surface","Large","Small")],
  Size != "0.2-0.5 mm" & Size != "1-2 mm" & Size != "2-5 mm" & Size != ">5 mm")# & Location != i)
f.HDI95.long <-
  melt(f.HDI95,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.HDI95.long$Size <- factor(f.HDI95.long$Size, levels = sizes)
f.HDI90 <-
  subset(
    posts$f$HDI90[c(variables,"Surface","Large","Small")],
  Size != "0.2-0.5 mm" & Size != "1-2 mm" & Size != "2-5 mm" & Size != ">5 mm")# & Location != i)
f.HDI90.long <-
  melt(f.HDI90,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.HDI90.long$Size <- factor(f.HDI90.long$Size, levels = sizes)
f.HDI75 <-
  subset(
    posts$f$HDI75[c(variables,"Surface","Large","Small")],
  Size != "0.2-0.5 mm" & Size != "1-2 mm" & Size != "2-5 mm" & Size != ">5 mm")# & Location != i)
f.HDI75.long <-
  melt(f.HDI75,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.HDI75.long$Size <- factor(f.HDI75.long$Size, levels = sizes)
f.HDI50 <-
  subset(
    posts$f$HDI50[c(variables,"Surface","Large","Small")],
  Size != "0.2-0.5 mm" & Size != "1-2 mm" & Size != "2-5 mm" & Size != ">5 mm")# & Location != i)
f.HDI50.long <-
  melt(f.HDI50,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.HDI50.long$Size <- factor(f.HDI50.long$Size, levels = sizes)

# Appending columns with the min and max of the 95% HDI to the mode data frame.
f.mode.long$min95 <- f.HDI95.long$f[seq(1,nrow(f.HDI95.long),2)]
f.mode.long$max95 <- f.HDI95.long$f[seq(2,nrow(f.HDI95.long),2)]

# print(
ggplot(mapping = 
         aes(x = f, y = Depth, color = Size, fill = Size, shape = Size, 
           group = interaction(Depth, Size)))+
  # geom_path(
  #   data=f.mode.long,
  #   aes(x=f, y=Depth, color = Size, group = interaction(Size)),
  #   size = 1, alpha = 1,
  #   position = position_dodgev(height = 100))+
  geom_line(
    data = f.HDI95.long,
    alpha = 0.5, size = 1,
    position = position_dodgev(height = 100))+
  geom_line(
    data = f.HDI90.long,
    alpha = 0.7, size = 1.5,
    position = position_dodgev(height = 100))+
  geom_line(
    data = f.HDI75.long,
    alpha = 1, size = 2,
    position = position_dodgev(height = 100))+
  geom_line(
    data = f.HDI50.long,
    alpha = 1, size = 3,
    position = position_dodgev(height = 100))+
  geom_point(
    data=f.mode.long,
    size = 2.5, color = "black",
    position = position_dodgev(height = 100))+
  scale_shape_manual(values = c(21,22,23,24,21,22,23,24,21,22,23,24))+
  facet_wrap(~ Source)+
  # facet_wrap(~ Source, nrow = 1)+
  scale_y_reverse(breaks = c(0,250,500,750,1000,1250,1500), minor_breaks = c())+
  scale_x_continuous(breaks = c(0,0.5,1), labels = c("0","0.5","1"))+
  coord_cartesian(ylim=c(NA,0))+
  scale_color_manual(breaks = sizes,
                     values = hue_pal()(length(sizes)))+
  scale_fill_manual(breaks = sizes,
                     values = hue_pal()(length(sizes)))+
  labs(color="Taxa",fill="Taxa",shape="Taxa")+
  theme_light()+theme(strip.text.x = element_text(size = 8),
                        axis.title.x = element_blank(),
                        axis.title.y = element_blank(),
                        plot.title = element_text(size=12, hjust=0.5))
}

plot.PAP <-
  f_depth_plots(posts.PAP) + ggtitle("North Atlantic")
plot.OSP <-
  f_depth_plots(posts.OSP) + ggtitle("Station Papa")
plot.ALOHAS <-
  f_depth_plots(posts.ALOHAS) + ggtitle("ALOHA Summer")
plot.ALOHAW <-
  f_depth_plots(posts.ALOHAW) + ggtitle("ALOHA Winter")
# plot.8N <-
#   f_depth_plots(posts.8N) + ggtitle("8 N")
# plot.5N <-
#   f_depth_plots(posts.5N) + ggtitle("5 N")

plot.blank <-
  ggplot+geom_blank()+theme_bw()+theme(panel.border=element_blank())

ggarrange(
  ggplot() + geom_blank() + ylab("Depth (m)"),

ggarrange(plot.OSP,    plot.PAP,
          plot.ALOHAS, plot.ALOHAW,
          #plot.5N,     plot.8N,
          ncol = 2, nrow = 2,
          common.legend = FALSE, legend="right"),

  ggplot() + geom_blank() + theme_void(),
  ggplot() + geom_blank() + xlab("Mixing Coefficients"),
  widths = c(0.04,1),
  heights = c(1,0.05)
)

# ggplot()+
#   # geom_path(
#   #   data=f.mode.long,
#   #   aes(x=f, y=Depth, color = Size, group = interaction(Size)),
#   #   size = 1, alpha = 1,
#   #   position = position_dodgev(height = 100))+
#   geom_line(
#     data = f.HDI95,
#     aes(x = Surface, y = Depth, color = Location, group = interaction(Depth, Size)),
#     alpha = 0.5, size = 1,
#     position = position_dodgev(height = 100))+
#   geom_line(
#     data = f.HDI90,
#     aes(x = Surface, y = Depth, color = Location, group = interaction(Depth, Size)),
#     alpha = 0.7, size = 1.5,
#     position = position_dodgev(height = 100))+
#   geom_line(
#     data = f.HDI75,
#     aes(x = Surface, y = Depth, color = Location, group = interaction(Depth, Size)),
#     alpha = 1, size = 2,
#     position = position_dodgev(height = 100))+
#   geom_line(
#     data = f.HDI50,
#     aes(x = Surface, y = Depth, color = Location, group = interaction(Depth, Size)),
#     alpha = 1, size = 3,
#     position = position_dodgev(height = 100))+
#   geom_point(
#     data=f.mode,
#     aes(x=Surface, y=Depth, fill = Location, group = interaction(Depth, Size)),
#     size = 2.5, shape = 22,
#     position = position_dodgev(height = 100))+
#   labs()+
#   facet_wrap(~ Size, nrow=2)+
#   # facet_wrap(~ Source, nrow = 1)+
#   scale_y_reverse(breaks = c(0,250,500,750,1000,1250,1500), minor_breaks = c())+
#   scale_x_continuous(breaks = c(0,0.5,1), labels = c("0","0.5","1"))+
#   coord_cartesian(ylim=c(NA,0))+
#   theme_light()

noquote("Some summary stats:")

noquote("OSP Carnivores")
min(subset(posts.OSP$f$mode , Size == "Chaetognath" | Size == "Radiolarian")$Surface)
mean(subset(posts.OSP$f$mode , Size == "Chaetognath" | Size == "Radiolarian")$Surface)
max(subset(posts.OSP$f$mode , Size == "Chaetognath" | Size == "Radiolarian")$Surface)

noquote("OSP Metridia")
subset(posts.OSP$f$mode , Size == "Metridia")$Surface

noquote("PAP Carnivores, Migrators, Detritivores")
min(subset(posts.PAP$f$mode , Size == "Chaetognath" | Size == "Metridia" | Size == "Pleuromamma" | Size == "Oncaeid")$Surface)
mean(subset(posts.PAP$f$mode , Size == "Chaetognath" | Size == "Metridia" | Size == "Pleuromamma" | Size == "Oncaeid")$Surface)
max(subset(posts.PAP$f$mode , Size == "Chaetognath" | Size == "Metridia" | Size == "Pleuromamma" | Size == "Oncaeid")$Surface)

noquote("PAP Oncaeia")
min(subset(posts.PAP$f$mode , Size == "Oncaeid")$Surface)
mean(subset(posts.PAP$f$mode , Size == "Oncaeid")$Surface)
max(subset(posts.PAP$f$mode , Size == "Oncaeid")$Surface)

noquote("Gaetanus at 225 m")
subset(posts.PAP$f$mode , Size == "Gaetanus" & Depth == 225)$Surface

noquote("Gaetanus at 625 m")
subset(posts.PAP$f$mode , Size == "Gaetanus" & Depth == 625)$Surface

noquote("ALOHA Chaetognaths, Harpactacoids, and Pleuromamma")
min(subset(rbind(posts.ALOHAS$f$mode,posts.ALOHAW$f$mode) , (Size == "Chaetognath" & Depth<1000) | Size == "Harpactacoid" | Size == "Pleuromamma")$Surface)
mean(subset(rbind(posts.ALOHAS$f$mode,posts.ALOHAW$f$mode) , (Size == "Chaetognath" & Depth<1000) | Size == "Harpactacoid" | Size == "Pleuromamma")$Surface)
max(subset(rbind(posts.ALOHAS$f$mode,posts.ALOHAW$f$mode) , (Size == "Chaetognath" & Depth<1000) | Size == "Harpactacoid" | Size == "Pleuromamma")$Surface)

```

Next we're going to make depth profiles, comparing the mixing model results at all five locations.

```{r f_depth_profiles_1-2, DPI = 300, fig.width=8.5, fig.asp=0.4, warning =FALSE, cache=FALSE, eval=FALSE}
# # Because submicron particles were not collected at 5N and 8N, we will make a
# # column call "Small" which we can compare to mixing model resuls from
# # other location where small and submicron particles are pooled.
# posts.5N$f$mode$Small <- posts.5N$f$mode$Small
# posts.8N$f$mode$Small <- posts.8N$f$mode$Small
# posts.5N$f$HDI95$Small <- posts.5N$f$HDI95$Small
# posts.8N$f$HDI95$Small <- posts.8N$f$HDI95$Small
# posts.5N$f$HDI90$Small <- posts.5N$f$HDI90$Small
# posts.8N$f$HDI90$Small <- posts.8N$f$HDI90$Small
# posts.5N$f$HDI75$Small <- posts.5N$f$HDI75$Small
# posts.8N$f$HDI75$Small <- posts.8N$f$HDI75$Small
# posts.5N$f$HDI50$Small <- posts.5N$f$HDI50$Small
# posts.8N$f$HDI50$Small <- posts.8N$f$HDI50$Small

# Making master data frames including all locations
# Also putting those into long format for plotting
f.mode <- 
  subset(
    bind_rows(
    posts.5N$f$mode[c(variables,"Surface","Large","Small")],
    posts.8N$f$mode[c(variables,"Surface","Large","Small")],
    posts.ALOHAS$f$mode[c(variables,"Surface","Large","Small")],
    posts.ALOHAW$f$mode[c(variables,"Surface","Large","Small")],
    posts.OSP$f$mode[c(variables,"Surface","Large","Small")],
    posts.PAP$f$mode[c(variables,"Surface","Large","Small")]),
    Size == "1-2 mm")
f.mode.long <-
  melt(f.mode,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.HDI95 <- 
  subset(
    bind_rows(
    posts.5N$f$HDI95[c(variables,"Surface","Large","Small")],
    posts.8N$f$HDI95[c(variables,"Surface","Large","Small")],
    posts.ALOHAS$f$HDI95[c(variables,"Surface","Large","Small")],
    posts.ALOHAW$f$HDI95[c(variables,"Surface","Large","Small")],
    posts.OSP$f$HDI95[c(variables,"Surface","Large","Small")],
    posts.PAP$f$HDI95[c(variables,"Surface","Large","Small")]),
    Size == "1-2 mm")
f.HDI95.long <-
  melt(f.HDI95,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.HDI90 <- 
  subset(
    bind_rows(
    posts.5N$f$HDI90[c(variables,"Surface","Large","Small")],
    posts.8N$f$HDI90[c(variables,"Surface","Large","Small")],
    posts.ALOHAS$f$HDI90[c(variables,"Surface","Large","Small")],
    posts.ALOHAW$f$HDI90[c(variables,"Surface","Large","Small")],
    posts.OSP$f$HDI90[c(variables,"Surface","Large","Small")],
    posts.PAP$f$HDI90[c(variables,"Surface","Large","Small")]),
    Size == "1-2 mm")
f.HDI90.long <-
  melt(f.HDI90,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.HDI75 <- 
  subset(
    bind_rows(
    posts.5N$f$HDI75[c(variables,"Surface","Large","Small")],
    posts.8N$f$HDI75[c(variables,"Surface","Large","Small")],
    posts.ALOHAS$f$HDI75[c(variables,"Surface","Large","Small")],
    posts.ALOHAW$f$HDI75[c(variables,"Surface","Large","Small")],
    posts.OSP$f$HDI75[c(variables,"Surface","Large","Small")],
    posts.PAP$f$HDI75[c(variables,"Surface","Large","Small")]),
    Size == "1-2 mm")
f.HDI75.long <-
  melt(f.HDI75,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.HDI50 <- 
  subset(
    bind_rows(
    posts.5N$f$HDI50[c(variables,"Surface","Large","Small")],
    posts.8N$f$HDI50[c(variables,"Surface","Large","Small")],
    posts.ALOHAS$f$HDI50[c(variables,"Surface","Large","Small")],
    posts.ALOHAW$f$HDI50[c(variables,"Surface","Large","Small")],
    posts.OSP$f$HDI50[c(variables,"Surface","Large","Small")],
    posts.PAP$f$HDI50[c(variables,"Surface","Large","Small")]),
    Size == "1-2 mm")
f.HDI50.long <-
  melt(f.HDI50,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")

# Appending columns with the min and max of the 95% HDI to the mode data frame.
f.mode.long$min95 <- f.HDI95.long$f[seq(1,nrow(f.HDI95.long),2)]
f.mode.long$max95 <- f.HDI95.long$f[seq(2,nrow(f.HDI95.long),2)]

ggplot()+
  geom_colh(data = f.mode.long,
            aes(x=f, y=Depth, fill=Source),
            width = 90, color = "black")+
  # geom_errorbarh(data = f.mode.long,
  #                aes(x=f, y=Depth, fill=Source,
  #                    xmin = min95, xmax = max95),
  #                height=0,
  #                position = position_dodgev(height=90))+
  labs(color= "Organic Matter Source")+
  facet_wrap(~ Location, nrow=1)+
  scale_y_reverse(breaks = c(0,200,500,1000,1500), minor_breaks = c())+
  coord_cartesian(ylim=c(1500,0))+
  theme_light()
  
ggplot()+
  geom_path(
    data=f.mode.long,
    aes(x=f, y=Depth, color=Location),
    size = 1, alpha = 1,
    position = position_dodgev(height = 100))+
  geom_line(
    data = f.HDI95.long,
    aes(x = f, y = Depth, group = interaction(Depth, Location), 
        color = Location),
    alpha = 0.2, size = 1,
    position = position_dodgev(height = 100))+
  geom_line(
    data = f.HDI90.long,
    aes(x = f, y = Depth, group = interaction(Depth, Location), 
        color = Location),
    alpha = 0.2, size = 1.5,
    position = position_dodgev(height = 100))+
  geom_line(
    data = f.HDI75.long,
    aes(x = f, y = Depth, group = interaction(Depth, Location), 
        color = Location),
    alpha = 0.3, size = 2,
    position = position_dodgev(height = 100))+
  geom_line(
    data = f.HDI50.long,
    aes(x = f, y = Depth, group = interaction(Depth, Location), 
        color = Location),
    alpha = 0.5, size = 3,
    position = position_dodgev(height = 100))+
  geom_point(
    data=f.mode.long,
    aes(x=f, y=Depth, fill=Location),
    size = 2.5, shape = 22,
    position = position_dodgev(height = 100))+
  labs(color= "Location")+
  facet_wrap(~ Source, nrow=1)+
  scale_y_reverse(breaks = c(0,200,500,1000,1500), minor_breaks = c())+
  coord_cartesian(ylim=c(1500,0))+
  theme_light()

```

# Trophic Parameter Depth Profiles {-}

First we'll try and make a full page figure of all model results from all locations.

```{r trophic_depth_profiles, DPI = 300, fig.width=8.5, fig.asp=1, cache=FALSE}
# for (i in c("5 N","8 N","ALOHA S","ALOHA W","OSP")) {
# Making master data frames including all locations
# Also putting those into long format for plotting
sizes <- c("0.06-0.2 mm", "0.2-0.5 mm", "1-2 mm", "2-5 mm", ">5 mm",
           "Oithonid", "Harpactacoid", "Pleuromamma", "Peuromamma", "Ostracod", "Oncaeid", "Gaussia", "Chaetognath","Radiolarian", "Metridia", "Neocalanus","Gaetanus")
trophic.mode <- 
  subset(
  bind_rows(
    posts.5N$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.8N$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAS$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAW$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.OSP$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.PAP$trophic$mode[c(variables,"PTS","MTS","FWL")]),
  Size != "0.06-0.2 mm")# & Location == i)
trophic.mode.long <-
  melt(trophic.mode,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.mode.long$Size <- factor(trophic.mode.long$Size, levels = sizes)
trophic.HDI95 <- 
  subset(
    bind_rows(
    posts.5N$trophic$HDI95[c(variables,"PTS","MTS","FWL")],
    posts.8N$trophic$HDI95[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAS$trophic$HDI95[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAW$trophic$HDI95[c(variables,"PTS","MTS","FWL")],
    posts.OSP$trophic$HDI95[c(variables,"PTS","MTS","FWL")],
    posts.PAP$trophic$HDI95[c(variables,"PTS","MTS","FWL")]),
  Size != "0.06-0.2 mm")# & Location == i)
trophic.HDI95.long <-
  melt(trophic.HDI95,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.HDI95.long$Size <- factor(trophic.HDI95.long$Size, levels = sizes)
trophic.HDI90 <- 
  subset(
    bind_rows(
    posts.5N$trophic$HDI90[c(variables,"PTS","MTS","FWL")],
    posts.8N$trophic$HDI90[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAS$trophic$HDI90[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAW$trophic$HDI90[c(variables,"PTS","MTS","FWL")],
    posts.OSP$trophic$HDI90[c(variables,"PTS","MTS","FWL")],
    posts.PAP$trophic$HDI90[c(variables,"PTS","MTS","FWL")]),
  Size != "0.06-0.2 mm")# & Location == i)
trophic.HDI90.long <-
  melt(trophic.HDI90,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.HDI90.long$Size <- factor(trophic.HDI90.long$Size, levels = sizes)
trophic.HDI75 <- 
  subset(
    bind_rows(
    posts.5N$trophic$HDI75[c(variables,"PTS","MTS","FWL")],
    posts.8N$trophic$HDI75[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAS$trophic$HDI75[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAW$trophic$HDI75[c(variables,"PTS","MTS","FWL")],
    posts.OSP$trophic$HDI75[c(variables,"PTS","MTS","FWL")],
    posts.PAP$trophic$HDI75[c(variables,"PTS","MTS","FWL")]),
  Size != "0.06-0.2 mm")# & Location == i)
trophic.HDI75.long <-
  melt(trophic.HDI75,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.HDI75.long$Size <- factor(trophic.HDI75.long$Size, levels = sizes)
trophic.HDI50 <- 
  subset(
    bind_rows(
    posts.5N$trophic$HDI50[c(variables,"PTS","MTS","FWL")],
    posts.8N$trophic$HDI50[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAS$trophic$HDI50[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAW$trophic$HDI50[c(variables,"PTS","MTS","FWL")],
    posts.OSP$trophic$HDI50[c(variables,"PTS","MTS","FWL")],
    posts.PAP$trophic$HDI50[c(variables,"PTS","MTS","FWL")]),
  Size != "0.06-0.2 mm")# & Location == i)
trophic.HDI50.long <-
  melt(trophic.HDI50,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.HDI50.long$Size <- factor(trophic.HDI50.long$Size, levels = sizes)

# Appending columns with the min and max of the 95% HDI to the mode data frame.
trophic.mode.long$min95 <- trophic.HDI95.long$trophic[seq(1,nrow(trophic.HDI95.long),2)]
trophic.mode.long$max95 <- trophic.HDI95.long$trophic[seq(2,nrow(trophic.HDI95.long),2)]
  
# # print(
# ggplot()+
#   # geom_path(
#   #   data=trophic.mode.long,
#   #   aes(x=f, y=Depth, color = Size, group = interaction(Size)),
#   #   size = 1, alpha = 1,
#   #   position = position_dodgev(height = 100))+
#   geom_line(
#     data = trophic.HDI95.long,
#     aes(x = value, y = Depth, color = Size, group = interaction(Depth, Size)),
#     alpha = 0.5, size = 1,
#     position = position_dodgev(height = 100))+
#   geom_line(
#     data = trophic.HDI90.long,
#     aes(x = value, y = Depth, color = Size, group = interaction(Depth, Size)),
#     alpha = 0.7, size = 1.5,
#     position = position_dodgev(height = 100))+
#   geom_line(
#     data = trophic.HDI75.long,
#     aes(x = value, y = Depth, color = Size, group = interaction(Depth, Size)),
#     alpha = 1, size = 2,
#     position = position_dodgev(height = 100))+
#   geom_line(
#     data = trophic.HDI50.long,
#     aes(x = value, y = Depth, color = Size, group = interaction(Depth, Size)),
#     alpha = 1, size = 3,
#     position = position_dodgev(height = 100))+
#   geom_point(
#     data=trophic.mode.long,
#     aes(x = value, y = Depth, fill = Size, group = interaction(Depth, Size)),
#     size = 2.5, shape = 22,
#     position = position_dodgev(height = 100))+
#   labs()+
#   facet_grid(cols = vars(Source), 
#              rows = vars(factor(Location, levels = c("OSP","ALOHA S","ALOHA W","8 N","5 N"))),
#              scales = "free")+
#   scale_y_reverse(breaks = c(0,250,500,750,1000,1250,1500), minor_breaks = c())+
#   scale_x_continuous(breaks = c(0,1,2,3,4,5), minor_breaks = c(0.5,1.5,2.6,3.5,4.5))+
#   coord_cartesian(ylim=c(NA,0), xlim=c(0,NA))+
#   xlab("Trophic Parameter")+
#   theme_light()
# # )
# # }

trophic_depth_plots <- function(
    posts
){
  trophic.mode <- 
  subset(
    posts$trophic$mode[c(variables,"FWL","PTS","MTS")],
  Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")# & Location == i)
trophic.mode.long <-
  melt(trophic.mode,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.mode.long$Size <- factor(trophic.mode.long$Size, levels = sizes)
trophic.HDI95 <- 
  subset(
    posts$trophic$HDI95[c(variables,"FWL","PTS","MTS")],
  Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")# & Location == i)
trophic.HDI95.long <-
  melt(trophic.HDI95,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.HDI95.long$Size <- factor(trophic.HDI95.long$Size, levels = sizes)
trophic.HDI90 <- 
  subset(
    posts$trophic$HDI90[c(variables,"FWL","PTS","MTS")],
  Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")# & Location == i)
trophic.HDI90.long <-
  melt(trophic.HDI90,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.HDI90.long$Size <- factor(trophic.HDI90.long$Size, levels = sizes)
trophic.HDI75 <- 
  subset(
    posts$trophic$HDI75[c(variables,"FWL","PTS","MTS")],
  Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")# & Location == i)
trophic.HDI75.long <-
  melt(trophic.HDI75,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.HDI75.long$Size <- factor(trophic.HDI75.long$Size, levels = sizes)
trophic.HDI50 <- 
  subset(
    posts$trophic$HDI50[c(variables,"FWL","PTS","MTS")],
  Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")# & Location == i)
trophic.HDI50.long <-
  melt(trophic.HDI50,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.HDI50.long$Size <- factor(trophic.HDI50.long$Size, levels = sizes)

# Appending columns with the min and max of the 95% HDI to the mode data frame.
trophic.mode.long$min95 <- trophic.HDI95.long$trophic[seq(1,nrow(trophic.HDI95.long),2)]
trophic.mode.long$max95 <- trophic.HDI95.long$trophic[seq(2,nrow(trophic.HDI95.long),2)]

sizes <- c("0.2-0.5 mm", "1-2 mm", "2-5 mm", ">5 mm")

# print(
ggplot()+
  # geom_path(
  #   data=trophic.mode.long,
  #   aes(x=f, y=Depth, color = Size, group = interaction(Size)),
  #   size = 1, alpha = 1,
  #   position = position_dodgev(height = 100))+
  geom_line(
    data = trophic.HDI95.long,
    aes(x = value, y = Depth, color = Size, group = interaction(Depth, Size)),
    alpha = 0.5, size = 1,
    position = position_dodgev(height = 100))+
  geom_line(
    data = trophic.HDI90.long,
    aes(x = value, y = Depth, color = Size, group = interaction(Depth, Size)),
    alpha = 0.7, size = 1.5,
    position = position_dodgev(height = 100))+
  geom_line(
    data = trophic.HDI75.long,
    aes(x = value, y = Depth, color = Size, group = interaction(Depth, Size)),
    alpha = 1, size = 2,
    position = position_dodgev(height = 100))+
  geom_line(
    data = trophic.HDI50.long,
    aes(x = value, y = Depth, color = Size, group = interaction(Depth, Size)),
    alpha = 1, size = 3,
    position = position_dodgev(height = 100))+
  geom_point(
    data=trophic.mode.long,
    aes(x = value, y=Depth, fill = Size, group = interaction(Depth, Size)),
    size = 2.5, shape = 22,
    position = position_dodgev(height = 100))+
  labs()+
  facet_wrap(~ Source)+
  # facet_wrap(~ Source, nrow = 1)+
  scale_y_reverse(breaks = c(0,250,500,750,1000,1250,1500), minor_breaks = c())+
  scale_x_continuous(breaks = seq(-1,5,0.5), 
                     labels = c("-1","","0","","1","","2","","3","","4","","5"))+
  scale_color_manual(breaks = sizes,
                     values = hue_pal()(length(sizes)))+
  scale_fill_manual(breaks = sizes,
                    values = hue_pal()(length(sizes)))+
  coord_cartesian(ylim=c(NA,-50), xlim=c(0,NA), expand=FALSE)+
  theme_light()+theme(strip.text.x = element_text(size = 8),
                      axis.title.x = element_blank(),
                      axis.title.y = element_blank(),
                      plot.title = element_text(size=12, hjust=0.5))
}

# alternative plot plotting colors
  # scale_color_manual(breaks = sizes,
  #                    values = c("goldenrod1","darkorange2","maroon3","purple1"))+
  # scale_fill_manual(breaks = sizes,
  #                    values = c("goldenrod1","darkorange2","maroon3","purple1"))+

plot.PAP <-
  trophic_depth_plots(posts.PAP) + ggtitle("North Atlantic")+
  coord_cartesian(ylim=c(1000,-50), expand = FALSE)
plot.OSP <-
  trophic_depth_plots(posts.OSP) + ggtitle("Station Papa")+
  coord_cartesian(ylim=c(1000,-50), expand = FALSE)
plot.ALOHAS <-
  trophic_depth_plots(posts.ALOHAS) + ggtitle("ALOHA Summer")
plot.ALOHAW <-
  trophic_depth_plots(posts.ALOHAW) + ggtitle("ALOHA Winter")
plot.8N <-
  trophic_depth_plots(posts.8N) + ggtitle("8° N")
plot.5N <-
  trophic_depth_plots(posts.5N) + ggtitle("5° N")

plot.blank <-
  ggplot+geom_blank()+theme_bw()+theme(panel.border=element_blank())

ggarrange(
  ggplot() + geom_blank() + ylab("Depth (m)"),

ggarrange(plot.OSP,    plot.PAP,
          plot.ALOHAS, plot.ALOHAW,
          plot.5N,     plot.8N,
          ncol = 2, nrow=3,
          common.legend = TRUE, legend="top"),
  
  ggplot() + geom_blank() + theme_void(),
  ggplot() + geom_blank() + xlab("Trophic Parameters"),
  widths = c(0.03,1),
  heights = c(1,0.05)
)
```

```{r trophic_depth_profiles_v2, DPI = 300, fig.width=5, fig.height=6, cache=FALSE}
# for (i in c("5 N","8 N","ALOHA S","ALOHA W","OSP")) {
# Making master data frames including all locations
# Also putting those into long format for plotting
sizes <- c("0.06-0.2 mm", "0.2-0.5 mm", "1-2 mm", "2-5 mm", ">5 mm",
           "Oithonid", "Harpactacoid", "Pleuromamma", "Peuromamma", "Ostracod", "Oncaeid", "Gaussia", "Chaetognath","Radiolarian", "Metridia", "Neocalanus","Gaetanus")
trophic.mode <- 
  subset(
  bind_rows(
    posts.5N$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.8N$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAS$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAW$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.OSP$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.PAP$trophic$mode[c(variables,"PTS","MTS","FWL")]),
  Size != "0.06-0.2 mm")# & Location == i)
trophic.mode$Location <- factor(trophic.mode$Location)
trophic.mode$Location[which(trophic.mode$Location == "Station P")] <- "Station Papa"
levels(trophic.mode$Location) <- c("5° N","8° N","ALOHA S","ALOHA W","Station Papa","N Atlantic")
# Let's calculate TP at the base of the food web
base.mode <- 
  subset(
  bind_rows(
    posts.5N$base$mode[c(variables,"d15NAla","d15NPhe")],
    posts.8N$base$mode[c(variables,"d15NAla","d15NPhe")],
    posts.ALOHAS$base$mode[c(variables,"d15NAla","d15NPhe")],
    posts.ALOHAW$base$mode[c(variables,"d15NAla","d15NPhe")],
    posts.OSP$base$mode[c(variables,"d15NAla","d15NPhe")],
    posts.PAP$base$mode[c(variables,"d15NAla","d15NPhe")]),
  Size != "0.06-0.2 mm")# & Location == i)
trophic.mode$baseTP <- (base.mode$d15NAla - base.mode$d15NPhe - 3.2) / 6.3 + 1
trophic.mode$Size <- factor(trophic.mode$Size, levels = sizes)
trophic.mode.long <-
  melt(trophic.mode,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.mode.long$Size <- factor(trophic.mode.long$Size, levels = sizes)

data.all$TP <- (data.all$d15NAla - data.all$d15NPhe - 3.2) / 6.3 + 1

trophic.mode.mean <- aggregate(
  x = cbind(FWL,baseTP) ~ Depth + Location,
  data = subset(trophic.mode,
                Size == "0.2-0.5 mm" | Size == "1-2 mm" | 
                  Size == "2-5 mm" | Size == ">5 mm"),
  FUN = "mean"
)
trophic.mode.range <- aggregate(
  x = cbind(FWL,baseTP) ~ Depth + Location,
  data = subset(trophic.mode,
                Size == "0.2-0.5 mm" | Size == "1-2 mm" | 
                  Size == "2-5 mm" | Size == ">5 mm"),
  FUN = "range"
)
trophic.mode.range$FWLstr <- NA
trophic.mode.range$baseTPstr <- NA
for (i in 1:nrow(trophic.mode.range)) {
  if (round(trophic.mode.range$FWL[i,1],1) == 
      round(trophic.mode.range$FWL[i,2],1)) {
    trophic.mode.range$FWLstr[i] <- round(trophic.mode.range[i,3],1)
  } else {
    trophic.mode.range$FWLstr[i] <-
      paste(round(trophic.mode.range$FWL[i,1],1),"-", 
      round(trophic.mode.range$FWL[i,2],1), sep=" ")
  }
  if (round(trophic.mode.range$baseTP[i,1],1) == 
      round(trophic.mode.range$baseTP[i,2],1)) {
    trophic.mode.range$baseTPstr[i] <- round(trophic.mode.range[i,4],1)
  } else {
    trophic.mode.range$baseTPstr[i] <-
      paste(round(trophic.mode.range$baseTP[i,1],1),"-", 
      round(trophic.mode.range$baseTP[i,2],1), sep=" ")
  }
}
trophic.mode.range$FWL <- trophic.mode.mean$FWL
trophic.mode.range$baseTP <- trophic.mode.mean$baseTP

ggplot(
  data = subset(trophic.mode,
                Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")
) +
  geom_colh(
    aes(x = FWL+baseTP, y = Depth, group = Size, fill = "FWL"),
    position = "dodgev", width = 90,
  )+
  geom_text(
    data = trophic.mode.range,
    aes(x = (FWL/2+baseTP), y = Depth, label = round(FWL,1), color = "FWL")
  )+
  geom_colh(
    aes(x = baseTP, y = Depth, group = Size, fill = "Base TP"),
    position = "dodgev", width = 90,
  )+
  geom_text(
    data = trophic.mode.range,
    aes(x = baseTP/2, y = Depth, label = round(baseTP,1), color = "Base TP")
    )+
  scale_fill_manual(values = c("steelblue","goldenrod"))+
  scale_color_manual(values = c("lightblue1","darkorange4"))+
  # geom_colh(
  #   data = subset(data.all,
  #               Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm"),
  #   aes(x = TP, y = Depth+20, group = Size),
  #   position = "dodgev", width = 40, fill = "goldenrod"
  # )+
  scale_y_reverse()+
  facet_wrap(~Location, nrow=2, dir = "v")+
  labs(fill="",color="") +
  theme(legend.position = "bottom") +
  xlab("Base TP + Food Web Length") + ylab("Depth (m)")

```


```{r trophic_depth_profiles_taxa, DPI = 300, fig.width=8.5, fig.height=6, cache=FALSE}
# for (i in c("5 N","8 N","ALOHA S","ALOHA W","OSP")) {
# Making master data frames including all locations
# Also putting those into long format for plotting
sizes <- c("0.06-0.2 mm", "0.2-0.5 mm", "1-2 mm", "2-5 mm", ">5 mm",
           "Oithonid", "Harpactacoid", "Pleuromamma", "Peuromamma", "Ostracod", "Oncaeid", "Gaussia", "Chaetognath","Radiolarian", "Metridia", "Neocalanus","Gaetanus")
trophic.mode <-
  subset(
  bind_rows(
    posts.5N$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.8N$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAS$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAW$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.OSP$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.PAP$trophic$mode[c(variables,"PTS","MTS","FWL")]),
  Size != "0.06-0.2 mm")# & Location == i)
trophic.mode.long <-
  melt(trophic.mode,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.mode.long$Size <- factor(trophic.mode.long$Size, levels = sizes)
trophic.HDI95 <-
  subset(
    bind_rows(
    posts.5N$trophic$HDI95[c(variables,"PTS","MTS","FWL")],
    posts.8N$trophic$HDI95[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAS$trophic$HDI95[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAW$trophic$HDI95[c(variables,"PTS","MTS","FWL")],
    posts.OSP$trophic$HDI95[c(variables,"PTS","MTS","FWL")],
    posts.PAP$trophic$HDI95[c(variables,"PTS","MTS","FWL")]),
  Size != "0.06-0.2 mm")# & Location == i)
trophic.HDI95.long <-
  melt(trophic.HDI95,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.HDI95.long$Size <- factor(trophic.HDI95.long$Size, levels = sizes)
trophic.HDI90 <-
  subset(
    bind_rows(
    posts.5N$trophic$HDI90[c(variables,"PTS","MTS","FWL")],
    posts.8N$trophic$HDI90[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAS$trophic$HDI90[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAW$trophic$HDI90[c(variables,"PTS","MTS","FWL")],
    posts.OSP$trophic$HDI90[c(variables,"PTS","MTS","FWL")],
    posts.PAP$trophic$HDI90[c(variables,"PTS","MTS","FWL")]),
  Size != "0.06-0.2 mm")# & Location == i)
trophic.HDI90.long <-
  melt(trophic.HDI90,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.HDI90.long$Size <- factor(trophic.HDI90.long$Size, levels = sizes)
trophic.HDI75 <-
  subset(
    bind_rows(
    posts.5N$trophic$HDI75[c(variables,"PTS","MTS","FWL")],
    posts.8N$trophic$HDI75[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAS$trophic$HDI75[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAW$trophic$HDI75[c(variables,"PTS","MTS","FWL")],
    posts.OSP$trophic$HDI75[c(variables,"PTS","MTS","FWL")],
    posts.PAP$trophic$HDI75[c(variables,"PTS","MTS","FWL")]),
  Size != "0.06-0.2 mm")# & Location == i)
trophic.HDI75.long <-
  melt(trophic.HDI75,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.HDI75.long$Size <- factor(trophic.HDI75.long$Size, levels = sizes)
trophic.HDI50 <-
  subset(
    bind_rows(
    posts.5N$trophic$HDI50[c(variables,"PTS","MTS","FWL")],
    posts.8N$trophic$HDI50[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAS$trophic$HDI50[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAW$trophic$HDI50[c(variables,"PTS","MTS","FWL")],
    posts.OSP$trophic$HDI50[c(variables,"PTS","MTS","FWL")],
    posts.PAP$trophic$HDI50[c(variables,"PTS","MTS","FWL")]),
  Size != "0.06-0.2 mm")# & Location == i)
trophic.HDI50.long <-
  melt(trophic.HDI50,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.HDI50.long$Size <- factor(trophic.HDI50.long$Size, levels = sizes)

# Appending columns with the min and max of the 95% HDI to the mode data frame.
trophic.mode.long$min95 <- trophic.HDI95.long$trophic[seq(1,nrow(trophic.HDI95.long),2)]
trophic.mode.long$max95 <- trophic.HDI95.long$trophic[seq(2,nrow(trophic.HDI95.long),2)]
#   
# # print(
# ggplot()+
#   # geom_path(
#   #   data=trophic.mode.long,
#   #   aes(x=f, y=Depth, color = Size, group = interaction(Size)),
#   #   size = 1, alpha = 1,
#   #   position = position_dodgev(height = 100))+
#   geom_line(
#     data = trophic.HDI95.long,
#     aes(x = value, y = Depth, color = Size, group = interaction(Depth, Size)),
#     alpha = 0.5, size = 1,
#     position = position_dodgev(height = 100))+
#   geom_line(
#     data = trophic.HDI90.long,
#     aes(x = value, y = Depth, color = Size, group = interaction(Depth, Size)),
#     alpha = 0.7, size = 1.5,
#     position = position_dodgev(height = 100))+
#   geom_line(
#     data = trophic.HDI75.long,
#     aes(x = value, y = Depth, color = Size, group = interaction(Depth, Size)),
#     alpha = 1, size = 2,
#     position = position_dodgev(height = 100))+
#   geom_line(
#     data = trophic.HDI50.long,
#     aes(x = value, y = Depth, color = Size, group = interaction(Depth, Size)),
#     alpha = 1, size = 3,
#     position = position_dodgev(height = 100))+
#   geom_point(
#     data=trophic.mode.long,
#     aes(x = value, y = Depth, fill = Size, group = interaction(Depth, Size)),
#     size = 2.5, shape = 22,
#     position = position_dodgev(height = 100))+
#   labs()+
#   facet_grid(cols = vars(Source), 
#              rows = vars(factor(Location, levels = c("OSP","ALOHA S","ALOHA W","8 N","5 N"))),
#              scales = "free")+
#   scale_y_reverse(breaks = c(0,250,500,750,1000,1250,1500), minor_breaks = c())+
#   scale_x_continuous(breaks = c(0,1,2,3,4,5), minor_breaks = c(0.5,1.5,2.6,3.5,4.5))+
#   coord_cartesian(ylim=c(NA,0), xlim=c(-0.25,NA))+
#   xlab("Trophic Parameter")+
#   theme_light()
# # )
# # }

sizes <- c("Oithonid", "Harpactacoid", "Pleuromamma", "Peuromamma", "Ostracod", "Oncaeid", "Gaussia", "Chaetognath","Radiolarian", "Metridia", "Neocalanus","Gaetanus")

trophic_depth_plots <- function(
    posts
){
  trophic.mode <- 
  subset(
    posts$trophic$mode[c(variables,"FWL","PTS","MTS")],
  Size != "0.2-0.5 mm" & Size != "1-2 mm" & Size != "2-5 mm" & Size != ">5 mm")# & Location == i)
trophic.mode.long <-
  melt(trophic.mode,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.mode.long$Size <- factor(trophic.mode.long$Size, levels = sizes)
trophic.HDI95 <- 
  subset(
    posts$trophic$HDI95[c(variables,"FWL","PTS","MTS")],
  Size != "0.2-0.5 mm" & Size != "1-2 mm" & Size != "2-5 mm" & Size != ">5 mm")# & Location == i)
trophic.HDI95.long <-
  melt(trophic.HDI95,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.HDI95.long$Size <- factor(trophic.HDI95.long$Size, levels = sizes)
trophic.HDI90 <- 
  subset(
    posts$trophic$HDI90[c(variables,"FWL","PTS","MTS")],
  Size != "0.2-0.5 mm" & Size != "1-2 mm" & Size != "2-5 mm" & Size != ">5 mm")# & Location == i)
trophic.HDI90.long <-
  melt(trophic.HDI90,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.HDI90.long$Size <- factor(trophic.HDI90.long$Size, levels = sizes)
trophic.HDI75 <- 
  subset(
    posts$trophic$HDI75[c(variables,"FWL","PTS","MTS")],
  Size != "0.2-0.5 mm" & Size != "1-2 mm" & Size != "2-5 mm" & Size != ">5 mm")# & Location == i)
trophic.HDI75.long <-
  melt(trophic.HDI75,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.HDI75.long$Size <- factor(trophic.HDI75.long$Size, levels = sizes)
trophic.HDI50 <- 
  subset(
    posts$trophic$HDI50[c(variables,"FWL","PTS","MTS")],
  Size != "0.2-0.5 mm" & Size != "1-2 mm" & Size != "2-5 mm" & Size != ">5 mm")# & Location == i)
trophic.HDI50.long <-
  melt(trophic.HDI50,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.HDI50.long$Size <- factor(trophic.HDI50.long$Size, levels = sizes)

# Appending columns with the min and max of the 95% HDI to the mode data frame.
trophic.mode.long$min95 <- trophic.HDI95.long$trophic[seq(1,nrow(trophic.HDI95.long),2)]
trophic.mode.long$max95 <- trophic.HDI95.long$trophic[seq(2,nrow(trophic.HDI95.long),2)]

# print(
ggplot(mapping = 
         aes(x = value, y = Depth, color = Size, fill = Size, shape = Size, 
           group = interaction(Depth, Size)))+
  # geom_path(
  #   data=trophic.mode.long,
  #   aes(x=f, y=Depth, color = Size, group = interaction(Size)),
  #   size = 1, alpha = 1,
  #   position = position_dodgev(height = 100))+
  geom_line(
    data = trophic.HDI95.long,
    alpha = 0.5, size = 1,
    position = position_dodgev(height = 100))+
  geom_line(
    data = trophic.HDI90.long,
    alpha = 0.7, size = 1.5,
    position = position_dodgev(height = 100))+
  geom_line(
    data = trophic.HDI75.long,
    alpha = 1, size = 2,
    position = position_dodgev(height = 100))+
  geom_line(
    data = trophic.HDI50.long,
    alpha = 1, size = 3,
    position = position_dodgev(height = 100))+
  geom_point(
    data=trophic.mode.long,
    size = 2.5, color = "black",
    position = position_dodgev(height = 100))+
  scale_shape_manual(values = c(21,22,23,24,21,22,23,24,21,22,23,24))+
  labs(color="Taxa",fill="Taxa",shape="Taxa")+
  facet_wrap(~ Source)+
  # facet_wrap(~ Source, nrow = 1)+
  scale_y_reverse(breaks = c(0,250,500,750,1000,1250,1500), 
                  minor_breaks = c())+
  scale_x_continuous(breaks = seq(-1,5,0.5), 
                     minor_breaks = c(),
                     labels = c("-1","","0","","1","","2","","3","","4","","5"))+
  coord_cartesian(ylim=c(NA,0), xlim=c(0,3))+
  scale_color_manual(breaks = sizes,
                     values = hue_pal()(length(sizes)))+
  scale_fill_manual(breaks = sizes,
                    values = hue_pal()(length(sizes)))+
  theme_light()+theme(strip.text.x = element_text(size = 8),
                      axis.title.x = element_blank(),
                      axis.title.y = element_blank(),
                      plot.title = element_text(size=12, hjust=0.5))
}

plot.PAP <-
  trophic_depth_plots(posts.PAP) + ggtitle("PAP Epoch 3")
plot.OSP <-
  trophic_depth_plots(posts.OSP) + ggtitle("Station Papa")
plot.ALOHAS <-
  trophic_depth_plots(posts.ALOHAS) + ggtitle("ALOHA Summer")
plot.ALOHAW <-
  trophic_depth_plots(posts.ALOHAW) + ggtitle("ALOHA Winter")
# plot.8N <-
#   trophic_depth_plots(posts.8N) + ggtitle("8 N")
# plot.5N <-
#   trophic_depth_plots(posts.5N) + ggtitle("5 N")

plot.blank <-
  ggplot+geom_blank()+theme_bw()+theme(panel.border=element_blank())

ggarrange(
  ggplot() + geom_blank() + ylab("Depth (m)"),

ggarrange(plot.OSP,    plot.PAP,
          plot.ALOHAS, plot.ALOHAW,
          #plot.5N,     plot.8N,
          ncol = 2, nrow=2,
          common.legend = FALSE, legend="right"),

  ggplot() + geom_blank() + theme_void(),
  ggplot() + geom_blank() + xlab("Trophic Parameters"),
  widths = c(0.04,1),
  heights = c(1,0.05)
)
```
Next we're going to make depth profiles, comparing the mixing model results at all five locations.

```{r trophic_depth_profiles_1-2, DPI = 300, fig.width=8.5, fig.asp=0.4, warning=FALSE, eval=FALSE}
# # Because submicron particles were not collected at 5N and 8N, we will make a
# # column call "Small" which we can compare to mixing model resuls from
# # other location where small and submicron particles are pooled.
# posts.5N$trophic$mode$Small <- posts.5N$trophic$mode$Small
# posts.8N$trophic$mode$Small <- posts.8N$trophic$mode$Small
# posts.5N$trophic$HDI95$Small <- posts.5N$trophic$HDI95$Small
# posts.8N$trophic$HDI95$Small <- posts.8N$trophic$HDI95$Small
# posts.5N$trophic$HDI90$Small <- posts.5N$trophic$HDI90$Small
# posts.8N$trophic$HDI90$Small <- posts.8N$trophic$HDI90$Small
# posts.5N$trophic$HDI75$Small <- posts.5N$trophic$HDI75$Small
# posts.8N$trophic$HDI75$Small <- posts.8N$trophic$HDI75$Small
# posts.5N$trophic$HDI50$Small <- posts.5N$trophic$HDI50$Small
# posts.8N$trophic$HDI50$Small <- posts.8N$trophic$HDI50$Small

# Making master data frames including all locations
# Also putting those into long format for plotting
trophic.mode <- 
  subset(
    bind_rows(
    posts.5N$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.8N$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAS$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAW$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.OSP$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.PAP$trophic$mode[c(variables,"PTS","MTS","FWL")]),
    Size == "1-2 mm")
trophic.mode.long <-
  melt(trophic.mode,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.HDI95 <- 
  subset(
    bind_rows(
    posts.5N$trophic$HDI95[c(variables,"PTS","MTS","FWL")],
    posts.8N$trophic$HDI95[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAS$trophic$HDI95[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAW$trophic$HDI95[c(variables,"PTS","MTS","FWL")],
    posts.OSP$trophic$HDI95[c(variables,"PTS","MTS","FWL")],
    posts.PAP$trophic$HDI95[c(variables,"PTS","MTS","FWL")]),
    Size == "1-2 mm")
trophic.HDI95.long <-
  melt(trophic.HDI95,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.HDI90 <- 
  subset(
    bind_rows(
    posts.5N$trophic$HDI90[c(variables,"PTS","MTS","FWL")],
    posts.8N$trophic$HDI90[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAS$trophic$HDI90[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAW$trophic$HDI90[c(variables,"PTS","MTS","FWL")],
    posts.OSP$trophic$HDI90[c(variables,"PTS","MTS","FWL")],
    posts.PAP$trophic$HDI90[c(variables,"PTS","MTS","FWL")]),
    Size == "1-2 mm")
trophic.HDI90.long <-
  melt(trophic.HDI90,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.HDI75 <- 
  subset(
    bind_rows(
    posts.5N$trophic$HDI75[c(variables,"PTS","MTS","FWL")],
    posts.8N$trophic$HDI75[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAS$trophic$HDI75[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAW$trophic$HDI75[c(variables,"PTS","MTS","FWL")],
    posts.OSP$trophic$HDI75[c(variables,"PTS","MTS","FWL")],
    posts.PAP$trophic$HDI75[c(variables,"PTS","MTS","FWL")]),
    Size == "1-2 mm")
trophic.HDI75.long <-
  melt(trophic.HDI75,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.HDI50 <- 
  subset(
    bind_rows(
    posts.5N$trophic$HDI50[c(variables,"PTS","MTS","FWL")],
    posts.8N$trophic$HDI50[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAS$trophic$HDI50[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAW$trophic$HDI50[c(variables,"PTS","MTS","FWL")],
    posts.OSP$trophic$HDI50[c(variables,"PTS","MTS","FWL")],
    posts.PAP$trophic$HDI50[c(variables,"PTS","MTS","FWL")]),
    Size == "1-2 mm")
trophic.HDI50.long <-
  melt(trophic.HDI50,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")

# Appending columns with the min and max of the 95% HDI to the mode data frame.
trophic.mode.long$min95 <- trophic.HDI95.long$value[seq(1,nrow(trophic.HDI95.long),2)]
trophic.mode.long$max95 <- trophic.HDI95.long$value[seq(2,nrow(trophic.HDI95.long),2)]

ggplot()+
  geom_colh(data = trophic.mode.long,
            aes(x=value, y=Depth, fill=Source),
            position = "dodgev", width = 90, color = "black")+
  geom_errorbarh(data = trophic.mode.long,
                 aes(x=value, y=Depth, fill=Source,
                     xmin = min95, xmax = max95),
                 height=0,
                 position = position_dodgev(height=90))+
labs(color= "Organic Matter Source")+
  facet_wrap(~ Location, nrow=1)+
  scale_y_reverse(breaks = c(0,200,500,1000,1500), minor_breaks = c())+
  coord_cartesian(ylim=c(1500,0))+
  theme_light()
  
ggplot()+
  geom_path(
    data=trophic.mode.long,
    aes(x = value, y=Depth, color=Location),
    size = 1, alpha = 1,
    position = position_dodgev(height = 100))+
  geom_line(
    data = trophic.HDI95.long,
    aes(x = value, y = Depth, group = interaction(Depth, Location), 
        color = Location),
    alpha = 0.2, size = 1,
    position = position_dodgev(height = 100))+
  geom_line(
    data = trophic.HDI90.long,
    aes(x = value, y = Depth, group = interaction(Depth, Location), 
        color = Location),
    alpha = 0.2, size = 1.5,
    position = position_dodgev(height = 100))+
  geom_line(
    data = trophic.HDI75.long,
    aes(x = value, y = Depth, group = interaction(Depth, Location), 
        color = Location),
    alpha = 0.3, size = 2,
    position = position_dodgev(height = 100))+
  geom_line(
    data = trophic.HDI50.long,
    aes(x = value, y = Depth, group = interaction(Depth, Location), 
        color = Location),
    alpha = 0.5, size = 3,
    position = position_dodgev(height = 100))+
  geom_point(
    data=trophic.mode.long,
    aes(x = value, y=Depth, fill=Location),
    size = 2.5, shape = 22,
    position = position_dodgev(height = 100))+
  labs(color= "Location")+
  facet_wrap(~ Source, nrow=1)+
  scale_y_reverse(breaks = c(0,200,500,1000,1500), minor_breaks = c())+
  coord_cartesian(ylim=c(1500,0))+
  theme_light()

```

```{r Linear_Models_1-2_trophic, dpi=300, fig.width=8, fig.asp=0.6}

trophic.mode <- 
  subset(
  bind_rows(
    posts.5N$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.8N$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAS$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAW$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.OSP$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.PAP$trophic$mode[c(variables,"PTS","MTS","FWL")]),
  Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")

print("===== FWL =====")

ggplot(
  data = trophic.mode,
  aes(x = Depth, y = FWL, color = Location, fill = Location))+
  geom_smooth(
    method = "lm", se = FALSE, lty = 2)+
  geom_smooth(
    method = "lm", se = TRUE, color = "black", fill = "grey50")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  ggtitle("FWL")

LM <- lm(FWL ~ Location + Depth + Location:Depth,
         data = trophic.mode
)
print("----- SUMMARY -----")
summary(LM)
print("----- ANOVA -----")
anova(LM)
plot(allEffects(LM))

LM <- lm(FWL ~ Depth,
         data = trophic.mode
)
print("----- SUMMARY -----")
summary(LM)
print("----- ANOVA -----")
anova(LM)
plot(allEffects(LM))

print("===== MTS =====")
ggplot(
  data = trophic.mode,
  aes(x = Depth, y = MTS, color = Location, fill = Location))+
  geom_smooth(
    method = "lm", se = FALSE, lty = 2)+
  geom_smooth(
    method = "lm", se = TRUE, color = "black", fill = "grey50")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  ggtitle("MTS")

LM <- lm(MTS ~ Depth * Location,
         data = trophic.mode
)
print("----- SUMMARY -----")
summary(LM)
print("----- ANOVA -----")
anova(LM)
plot(allEffects(LM))

print("===== PTS =====")
ggplot(
  data = trophic.mode,
  aes(x = Depth, y = PTS, color = Location, fill = Location))+
  geom_smooth(
    method = "lm", se = FALSE, lty = 2)+
  geom_smooth(
    method = "lm", se = TRUE, color = "black", fill = "grey50")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  ggtitle("PTS")

LM <- lm(PTS ~ Depth * Location,
         data = trophic.mode
)
print("----- SUMMARY -----")
summary(LM)
print("----- ANOVA -----")
anova(LM)
plot(allEffects(LM))

```

# f(surface) vs FWL in specific taxa

Next thing we'll do is make a quick plot of f(surface) vs FWL for all the samples of specific taxa to see how we can summarize those two OMSM outputs.

```{r fsurf-vs-trophic, dpi = 300, fig.width=7, fig.height=4}

f.mode <-
  subset(
  bind_rows(
    posts.5N$f$mode[c(variables,"Surface","Large","Small")],
    posts.8N$f$mode[c(variables,"Surface","Large","Small")],
    posts.ALOHAS$f$mode[c(variables,"Surface","Large","Small")],
    posts.ALOHAW$f$mode[c(variables,"Surface","Large","Small")],
    posts.OSP$f$mode[c(variables,"Surface","Large","Small")],
    posts.PAP$f$mode[c(variables,"Surface","Large","Small")]),
  Size != "0.06-0.2 mm" & Size != "0.2-0.5 mm" & Size != "1-2 mm" & Size != "2-5 mm" & Size != ">5 mm")# & Location == i)

trophic.mode <-
  subset(
  bind_rows(
    posts.5N$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.8N$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAS$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAW$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.OSP$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.PAP$trophic$mode[c(variables,"PTS","MTS","FWL")]),
  Size != "0.06-0.2 mm" & Size != "0.2-0.5 mm" & Size != "1-2 mm" & Size != "2-5 mm" & Size != ">5 mm")# & Location == i)
base.mode <- 
  subset(
  bind_rows(
    posts.5N$base$mode[c(variables,"d15NAla","d15NPhe")],
    posts.8N$base$mode[c(variables,"d15NAla","d15NPhe")],
    posts.ALOHAS$base$mode[c(variables,"d15NAla","d15NPhe")],
    posts.ALOHAW$base$mode[c(variables,"d15NAla","d15NPhe")],
    posts.OSP$base$mode[c(variables,"d15NAla","d15NPhe")],
    posts.PAP$base$mode[c(variables,"d15NAla","d15NPhe")]),
  Size != "0.06-0.2 mm" & Size != "0.2-0.5 mm" & Size != "1-2 mm" & Size != "2-5 mm" & Size != ">5 mm")# & Location == i)
trophic.mode$baseTP <- (base.mode$d15NAla - base.mode$d15NPhe - 3.2) / 6.3 + 1

ftrophic.mode <- cbind(
  f.mode, trophic.mode[c("FWL","PTS","MTS","baseTP")]
)

library(ggforce)
hulls <- ftrophic.mode %>%
  group_by(Size) %>%
  slice(chull(Surface, baseTP+FWL))


ggplot(
  data = ftrophic.mode,
  aes(y = baseTP+FWL, x = Surface, fill = Size, shape = Location, group = Size)
)+
  # geom_polygon(aes(group = Size), color = NA, alpha = 0.5)+
  geom_shape(data = hulls, 
             alpha = 0.5, expand = 0.03, radius = 0.03)+
  geom_point(size = 3)+
  # geom_shape(data = hulls, 
  #            aes(y = baseTP),
  #            alpha = 0.2, expand = 0.03, radius = 0.03)+
  # geom_point(aes(y = baseTP), size = 3, alpha = 0.5)+
  # stat_ellipse(aes(group = Size, fill = Size), alpha = 0.5,
  #              level = 0.5, type = "norm", geom = "polygon")+
  # geom_mark_hull(aes(group = Size, fill = Size), expand=0)+
  
  scale_shape_manual(values = c(21,22,23,24,21,22,23,24,21,22,23,24))+
  # xlim(0,1)+ 
  ylim(2,5)+
  scale_x_continuous(breaks = c(0,0.5,1), limits = c(0,1))+
  ylab("modelled TP")+
  xlab("f(surface)")+
  theme(legend.box = "horizontal")
  # facet_wrap(~ Location)

```

# OSP/PAP Focused Depth Profiles {-}

We really only need to communicate size class distinctions at Station Papa and in the North Atlantic, so let's make a quick composite plot summarizing thos results.

```{r OSP-PAP_depth_profiles, DPI = 300, fig.width=8, fig.height=8, cache=FALSE}

sizes <- c("0.06-0.2 mm", "0.2-0.5 mm", "1-2 mm", "2-5 mm", ">5 mm",
           "Oithonid", "Harpactacoid", "Pleuromamma", "Peuromamma", "Ostracod", "Oncaeid", "Gaussia", "Chaetognath","Radiolarian", "Metridia", "Neocalanus","Gaetanus")

f_depth_plots <- function(
    posts
){
  f.mode <- 
    subset(
      posts$f$mode[c(variables,"Surface","Large","Small")],
      Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")# & Location == i)
  f.mode.long <-
    melt(f.mode,
         id.vars = c(variables),
         variable.name = "Source",
         value.name = "f")
  f.mode.long$Size <- factor(f.mode.long$Size, levels = sizes)
  f.HDI95 <- 
    subset(
      posts$f$HDI95[c(variables,"Surface","Large","Small")],
      Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")# & Location == i)
  f.HDI95.long <-
    melt(f.HDI95,
         id.vars = c(variables),
         variable.name = "Source",
         value.name = "f")
  f.HDI95.long$Size <- factor(f.HDI95.long$Size, levels = sizes)
  f.HDI90 <- 
    subset(
      posts$f$HDI90[c(variables,"Surface","Large","Small")],
      Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")# & Location == i)
  f.HDI90.long <-
    melt(f.HDI90,
         id.vars = c(variables),
         variable.name = "Source",
         value.name = "f")
  f.HDI90.long$Size <- factor(f.HDI90.long$Size, levels = sizes)
  f.HDI75 <- 
    subset(
      posts$f$HDI75[c(variables,"Surface","Large","Small")],
      Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")# & Location == i)
  f.HDI75.long <-
    melt(f.HDI75,
         id.vars = c(variables),
         variable.name = "Source",
         value.name = "f")
  f.HDI75.long$Size <- factor(f.HDI75.long$Size, levels = sizes)
  f.HDI50 <- 
    subset(
      posts$f$HDI50[c(variables,"Surface","Large","Small")],
      Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")# & Location == i)
  f.HDI50.long <-
    melt(f.HDI50,
         id.vars = c(variables),
         variable.name = "Source",
         value.name = "f")
  f.HDI50.long$Size <- factor(f.HDI50.long$Size, levels = sizes)
  
  # Appending columns with the min and max of the 95% HDI to the mode data frame.
  f.mode.long$min95 <- f.HDI95.long$f[seq(1,nrow(f.HDI95.long),2)]
  f.mode.long$max95 <- f.HDI95.long$f[seq(2,nrow(f.HDI95.long),2)]
  
  sizes <- c("0.2-0.5 mm", "1-2 mm", "2-5 mm", ">5 mm")
  
  # print(
  ggplot()+
    # geom_path(
    #   data=f.mode.long,
    #   aes(x=f, y=Depth, color = Size, group = interaction(Size)),
    #   size = 1, alpha = 1,
    #   position = position_dodgev(height = 100))+
    geom_line(
      data = f.HDI95.long,
      aes(x = f, y = Depth, color = Size, group = interaction(Depth, Size)),
      alpha = 0.5, size = 1,
      position = position_dodgev(height = 100))+
    geom_line(
      data = f.HDI90.long,
      aes(x = f, y = Depth, color = Size, group = interaction(Depth, Size)),
      alpha = 0.7, size = 1.5,
      position = position_dodgev(height = 100))+
    geom_line(
      data = f.HDI75.long,
      aes(x = f, y = Depth, color = Size, group = interaction(Depth, Size)),
      alpha = 1, size = 2,
      position = position_dodgev(height = 100))+
    geom_line(
      data = f.HDI50.long,
      aes(x = f, y = Depth, color = Size, group = interaction(Depth, Size)),
      alpha = 1, size = 3,
      position = position_dodgev(height = 100))+
    geom_point(
      data=f.mode.long,
      aes(x=f, y=Depth, fill = Size, group = interaction(Depth, Size)),
      size = 2.5, shape = 22,
      position = position_dodgev(height = 100))+
    labs()+
    facet_wrap(~ Source)+
    # facet_wrap(~ Source, nrow = 1)+
    scale_y_reverse(breaks = c(0,250,500,750,1000,1250,1500), minor_breaks = c())+
    scale_x_continuous(breaks = c(0,0.5,1), labels = c("0","0.5","1"), limits = c(0,1))+
    coord_cartesian(ylim=c(NA,0))+
    scale_color_manual(breaks = sizes,
                       values = hue_pal()(length(sizes)))+
    scale_fill_manual(breaks = sizes,
                      values = hue_pal()(length(sizes)))+
    theme_light()+
    theme(strip.text.x = element_text(size = 8, face = "bold"),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          plot.title = element_text(size=14, hjust=0.5))
}

trophic_depth_plots <- function(
    posts
){
  trophic.mode <- 
    subset(
      posts$trophic$mode[c(variables,"FWL","PTS","MTS")],
      Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")# & Location == i)
  trophic.mode.long <-
    melt(trophic.mode,
         id.vars = c(variables),
         variable.name = "Source",
         value.name = "value")
  trophic.mode.long$Size <- factor(trophic.mode.long$Size, levels = sizes)
  trophic.HDI95 <- 
    subset(
      posts$trophic$HDI95[c(variables,"FWL","PTS","MTS")],
      Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")# & Location == i)
  trophic.HDI95.long <-
    melt(trophic.HDI95,
         id.vars = c(variables),
         variable.name = "Source",
         value.name = "value")
  trophic.HDI95.long$Size <- factor(trophic.HDI95.long$Size, levels = sizes)
  trophic.HDI90 <- 
    subset(
      posts$trophic$HDI90[c(variables,"FWL","PTS","MTS")],
      Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")# & Location == i)
  trophic.HDI90.long <-
    melt(trophic.HDI90,
         id.vars = c(variables),
         variable.name = "Source",
         value.name = "value")
  trophic.HDI90.long$Size <- factor(trophic.HDI90.long$Size, levels = sizes)
  trophic.HDI75 <- 
    subset(
      posts$trophic$HDI75[c(variables,"FWL","PTS","MTS")],
      Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")# & Location == i)
  trophic.HDI75.long <-
    melt(trophic.HDI75,
         id.vars = c(variables),
         variable.name = "Source",
         value.name = "value")
  trophic.HDI75.long$Size <- factor(trophic.HDI75.long$Size, levels = sizes)
  trophic.HDI50 <- 
    subset(
      posts$trophic$HDI50[c(variables,"FWL","PTS","MTS")],
      Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")# & Location == i)
  trophic.HDI50.long <-
    melt(trophic.HDI50,
         id.vars = c(variables),
         variable.name = "Source",
         value.name = "value")
  trophic.HDI50.long$Size <- factor(trophic.HDI50.long$Size, levels = sizes)
  
  # Appending columns with the min and max of the 95% HDI to the mode data frame.
  trophic.mode.long$min95 <- trophic.HDI95.long$trophic[seq(1,nrow(trophic.HDI95.long),2)]
  trophic.mode.long$max95 <- trophic.HDI95.long$trophic[seq(2,nrow(trophic.HDI95.long),2)]
  
  sizes <- c("0.2-0.5 mm", "1-2 mm", "2-5 mm", ">5 mm")
  
  # print(
  ggplot()+
    # geom_path(
    #   data=trophic.mode.long,
    #   aes(x=f, y=Depth, color = Size, group = interaction(Size)),
    #   size = 1, alpha = 1,
    #   position = position_dodgev(height = 100))+
    geom_line(
      data = trophic.HDI95.long,
      aes(x = value, y = Depth, color = Size, group = interaction(Depth, Size)),
      alpha = 0.5, size = 1,
      position = position_dodgev(height = 100))+
    geom_line(
      data = trophic.HDI90.long,
      aes(x = value, y = Depth, color = Size, group = interaction(Depth, Size)),
      alpha = 0.7, size = 1.5,
      position = position_dodgev(height = 100))+
    geom_line(
      data = trophic.HDI75.long,
      aes(x = value, y = Depth, color = Size, group = interaction(Depth, Size)),
      alpha = 1, size = 2,
      position = position_dodgev(height = 100))+
    geom_line(
      data = trophic.HDI50.long,
      aes(x = value, y = Depth, color = Size, group = interaction(Depth, Size)),
      alpha = 1, size = 3,
      position = position_dodgev(height = 100))+
    geom_point(
      data=trophic.mode.long,
      aes(x = value, y=Depth, fill = Size, group = interaction(Depth, Size)),
      size = 2.5, shape = 22,
      position = position_dodgev(height = 100))+
    labs()+
    facet_wrap(~ Source)+
    # facet_wrap(~ Source, nrow = 1)+
    scale_y_reverse(breaks = c(0,250,500,750,1000,1250,1500), minor_breaks = c())+
    scale_x_continuous(breaks = seq(-1,5,1), 
                       minor_breaks = c(-0.5,5.5,1),
                       labels = c("-1","0","1","2","3","4","5"))+
    coord_cartesian(ylim=c(NA,0), xlim=c(0,NA))+
    scale_color_manual(breaks = sizes,
                       values = hue_pal()(length(sizes)))+
    scale_fill_manual(breaks = sizes,
                      values = hue_pal()(length(sizes)))+
    theme_light()+
    theme(strip.text.x = element_text(size = 8, face = "bold"),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          plot.title = element_text(size=14, hjust=0.5))
}

plot.PAP.f <-
  f_depth_plots(posts.PAP) + 
  ggtitle("Proportional Contributions") + 
  theme(axis.title.y = element_text(angle = 90, vjust = 3)) +
  ylab("Depth (m)")
plot.OSP.f <-
  f_depth_plots(posts.OSP) + 
  ggtitle("Proportional Contributions") + 
  theme(axis.title.y = element_text(angle = 90, vjust  = 3)) +
  ylab("Depth (m)")
# plot.ALOHAS <-
#   f_depth_plots(posts.ALOHAS) + ggtitle("ALOHA Summer")
# plot.ALOHAW <-
#   f_depth_plots(posts.ALOHAW) + ggtitle("ALOHA Winter")
# plot.8N <-
#   f_depth_plots(posts.8N) + ggtitle("8 N")
# plot.5N <-
#   f_depth_plots(posts.5N) + ggtitle("5 N")

plot.PAP.trophic <-
  trophic_depth_plots(posts.PAP) + ggtitle("Trophic Parameters")
plot.OSP.trophic <-
  trophic_depth_plots(posts.OSP) + ggtitle("Trophic Parameters")
# plot.ALOHAS <-
#   trophic_depth_plots(posts.ALOHAS) + ggtitle("ALOHA Summer")
# plot.ALOHAW <-
#   trophic_depth_plots(posts.ALOHAW) + ggtitle("ALOHA Winter")
# plot.8N <-
#   trophic_depth_plots(posts.8N) + ggtitle("8 N")
# plot.5N <-
#   trophic_depth_plots(posts.5N) + ggtitle("5 N")

plot.blank <-
  ggplot+geom_blank()+theme_bw()+theme(panel.border=element_blank())

ggarrange(
  
  ggplot() + geom_blank() + ggtitle("North Atlantic") +
    theme(plot.title = element_text(hjust = 0.5, face = "bold")),
  
  ggarrange(plot.PAP.f,    plot.PAP.trophic,
            # plot.ALOHAS, plot.ALOHAW,
            # plot.5N,     plot.8N,
            ncol = 2, nrow=1,
            common.legend = TRUE, legend="none"),
  
  ggplot() + geom_blank(),
  
  ggplot() + geom_blank() + ggtitle("Station Papa") +
    theme(plot.title = element_text(hjust = 0.5, face = "bold")),
  
  ggarrange(plot.OSP.f,    plot.OSP.trophic,
            # plot.ALOHAS, plot.ALOHAW,
            # plot.5N,     plot.8N,
            ncol = 2, nrow=1,
            common.legend = TRUE, legend="bottom"),
  
  nrow = 5, heights = c(0.1,1,0.05,0.1,1.5)
)
```

```{r OSP-PAP_biplots, DPI = 300, fig.width=5, fig.height=5, cache=FALSE}

sizes <- c("0.06-0.2 mm", "0.2-0.5 mm", "1-2 mm", "2-5 mm", ">5 mm",
           "Oithonid", "Harpactacoid", "Pleuromamma", "Peuromamma", "Ostracod", "Oncaeid", "Gaussia", "Chaetognath","Radiolarian", "Metridia", "Neocalanus","Gaetanus")
f.mode <-
  subset(
  bind_rows(
    posts.5N$f$mode[c(variables,"Surface","Large","Small")],
    posts.8N$f$mode[c(variables,"Surface","Large","Small")],
    posts.ALOHAS$f$mode[c(variables,"Surface","Large","Small")],
    posts.ALOHAW$f$mode[c(variables,"Surface","Large","Small")],
    posts.OSP$f$mode[c(variables,"Surface","Large","Small")],
    posts.PAP$f$mode[c(variables,"Surface","Large","Small")]),
  Size != "0.06-0.2 mm" & Size != "0.2-0.5 mm" & Size != "1-2 mm" & Size != "2-5 mm" & Size != ">5 mm")# & Location == i)
f.mode.long <-
  melt(f.mode,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.mode.long$Size <- factor(f.mode.long$Size, levels = sizes)
f.HDI95 <-
  subset(
    bind_rows(
    posts.5N$f$HDI95[c(variables,"Surface","Large","Small")],
    posts.8N$f$HDI95[c(variables,"Surface","Large","Small")],
    posts.ALOHAS$f$HDI95[c(variables,"Surface","Large","Small")],
    posts.ALOHAW$f$HDI95[c(variables,"Surface","Large","Small")],
    posts.OSP$f$HDI95[c(variables,"Surface","Large","Small")],
    posts.PAP$f$HDI95[c(variables,"Surface","Large","Small")]),
  Size != "0.06-0.2 mm" & Size != "0.2-0.5 mm" & Size != "1-2 mm" & Size != "2-5 mm" & Size != ">5 mm")# & Location == i)
f.HDI95.long <-
  melt(f.HDI95,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.HDI95.long$Size <- factor(f.HDI95.long$Size, levels = sizes)
f.HDI90 <-
  subset(
    bind_rows(
    posts.5N$f$HDI90[c(variables,"Surface","Large","Small")],
    posts.8N$f$HDI90[c(variables,"Surface","Large","Small")],
    posts.ALOHAS$f$HDI90[c(variables,"Surface","Large","Small")],
    posts.ALOHAW$f$HDI90[c(variables,"Surface","Large","Small")],
    posts.OSP$f$HDI90[c(variables,"Surface","Large","Small")],
    posts.PAP$f$HDI90[c(variables,"Surface","Large","Small")]),
  Size != "0.06-0.2 mm" & Size != "0.2-0.5 mm" & Size != "1-2 mm" & Size != "2-5 mm" & Size != ">5 mm")# & Location == i)
f.HDI90.long <-
  melt(f.HDI90,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.HDI90.long$Size <- factor(f.HDI90.long$Size, levels = sizes)
f.HDI75 <-
  subset(
    bind_rows(
    posts.5N$f$HDI75[c(variables,"Surface","Large","Small")],
    posts.8N$f$HDI75[c(variables,"Surface","Large","Small")],
    posts.ALOHAS$f$HDI75[c(variables,"Surface","Large","Small")],
    posts.ALOHAW$f$HDI75[c(variables,"Surface","Large","Small")],
    posts.OSP$f$HDI75[c(variables,"Surface","Large","Small")],
    posts.PAP$f$HDI75[c(variables,"Surface","Large","Small")]),
  Size != "0.06-0.2 mm" & Size != "0.2-0.5 mm" & Size != "1-2 mm" & Size != "2-5 mm" & Size != ">5 mm")# & Location == i)
f.HDI75.long <-
  melt(f.HDI75,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.HDI75.long$Size <- factor(f.HDI75.long$Size, levels = sizes)
f.HDI50 <-
  subset(
    bind_rows(
    posts.5N$f$HDI50[c(variables,"Surface","Large","Small")],
    posts.8N$f$HDI50[c(variables,"Surface","Large","Small")],
    posts.ALOHAS$f$HDI50[c(variables,"Surface","Large","Small")],
    posts.ALOHAW$f$HDI50[c(variables,"Surface","Large","Small")],
    posts.OSP$f$HDI50[c(variables,"Surface","Large","Small")],
    posts.PAP$f$HDI50[c(variables,"Surface","Large","Small")]),
  Size != "0.06-0.2 mm" & Size != "0.2-0.5 mm" & Size != "1-2 mm" & Size != "2-5 mm" & Size != ">5 mm")# & Location == i)
f.HDI50.long <-
  melt(f.HDI50,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "f")
f.HDI50.long$Size <- factor(f.HDI50.long$Size, levels = sizes)

# Appending columns with the min and max of the 95% HDI to the mode data frame.
f.mode.long$min95 <- f.HDI95.long$f[seq(1,nrow(f.HDI95.long),2)]
f.mode.long$max95 <- f.HDI95.long$f[seq(2,nrow(f.HDI95.long),2)]

trophic.mode <-
  subset(
  bind_rows(
    posts.5N$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.8N$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAS$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAW$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.OSP$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.PAP$trophic$mode[c(variables,"PTS","MTS","FWL")]),
  Size != "0.06-0.2 mm" & Size != "0.2-0.5 mm" & Size != "1-2 mm" & Size != "2-5 mm" & Size != ">5 mm")# & Location == i)
trophic.mode.long <-
  melt(trophic.mode,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.mode.long$Size <- factor(trophic.mode.long$Size, levels = sizes)
trophic.HDI95 <-
  subset(
    bind_rows(
    posts.5N$trophic$HDI95[c(variables,"PTS","MTS","FWL")],
    posts.8N$trophic$HDI95[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAS$trophic$HDI95[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAW$trophic$HDI95[c(variables,"PTS","MTS","FWL")],
    posts.OSP$trophic$HDI95[c(variables,"PTS","MTS","FWL")],
    posts.PAP$trophic$HDI95[c(variables,"PTS","MTS","FWL")]),
  Size != "0.06-0.2 mm" & Size != "0.2-0.5 mm" & Size != "1-2 mm" & Size != "2-5 mm" & Size != ">5 mm")# & Location == i)
trophic.HDI95.long <-
  melt(trophic.HDI95,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.HDI95.long$Size <- factor(trophic.HDI95.long$Size, levels = sizes)
trophic.HDI90 <-
  subset(
    bind_rows(
    posts.5N$trophic$HDI90[c(variables,"PTS","MTS","FWL")],
    posts.8N$trophic$HDI90[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAS$trophic$HDI90[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAW$trophic$HDI90[c(variables,"PTS","MTS","FWL")],
    posts.OSP$trophic$HDI90[c(variables,"PTS","MTS","FWL")],
    posts.PAP$trophic$HDI90[c(variables,"PTS","MTS","FWL")]),
  Size != "0.06-0.2 mm" & Size != "0.2-0.5 mm" & Size != "1-2 mm" & Size != "2-5 mm" & Size != ">5 mm")# & Location == i)
trophic.HDI90.long <-
  melt(trophic.HDI90,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.HDI90.long$Size <- factor(trophic.HDI90.long$Size, levels = sizes)
trophic.HDI75 <-
  subset(
    bind_rows(
    posts.5N$trophic$HDI75[c(variables,"PTS","MTS","FWL")],
    posts.8N$trophic$HDI75[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAS$trophic$HDI75[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAW$trophic$HDI75[c(variables,"PTS","MTS","FWL")],
    posts.OSP$trophic$HDI75[c(variables,"PTS","MTS","FWL")],
    posts.PAP$trophic$HDI75[c(variables,"PTS","MTS","FWL")]),
  Size != "0.06-0.2 mm" & Size != "0.2-0.5 mm" & Size != "1-2 mm" & Size != "2-5 mm" & Size != ">5 mm")# & Location == i)
trophic.HDI75.long <-
  melt(trophic.HDI75,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.HDI75.long$Size <- factor(trophic.HDI75.long$Size, levels = sizes)
trophic.HDI50 <-
  subset(
    bind_rows(
    posts.5N$trophic$HDI50[c(variables,"PTS","MTS","FWL")],
    posts.8N$trophic$HDI50[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAS$trophic$HDI50[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAW$trophic$HDI50[c(variables,"PTS","MTS","FWL")],
    posts.OSP$trophic$HDI50[c(variables,"PTS","MTS","FWL")],
    posts.PAP$trophic$HDI50[c(variables,"PTS","MTS","FWL")]),
  Size != "0.06-0.2 mm" & Size != "0.2-0.5 mm" & Size != "1-2 mm" & Size != "2-5 mm" & Size != ">5 mm")# & Location == i)
trophic.HDI50.long <-
  melt(trophic.HDI50,
       id.vars = c(variables),
       variable.name = "Source",
       value.name = "value")
trophic.HDI50.long$Size <- factor(trophic.HDI50.long$Size, levels = sizes)

# Appending columns with the min and max of the 95% HDI to the mode data frame.
trophic.mode.long$min95 <- trophic.HDI95.long$trophic[seq(1,nrow(trophic.HDI95.long),2)]
trophic.mode.long$max95 <- trophic.HDI95.long$trophic[seq(2,nrow(trophic.HDI95.long),2)]

biplot.data <- f.mode[1:7]
biplot.data$Surface <- f.mode$Surface
biplot.data$SurfaceMin <- f.HDI95$Surface[seq(1,nrow(f.HDI95),2)]
biplot.data$SurfaceMax <- f.HDI95$Surface[seq(2,nrow(f.HDI95),2)]
biplot.data$FWL <- trophic.mode$FWL
biplot.data$FWLMin <- trophic.HDI95$FWL[seq(1,nrow(trophic.HDI95),2)]
biplot.data$FWLMax <- trophic.HDI95$FWL[seq(2,nrow(trophic.HDI95),2)]

biplot.data$Clade <- NA
biplot.data[which(
  biplot.data$Size == "Chaetognath" | biplot.data$Size == "Gaetanus"
  ),]$Clade <- "Carnivore"
biplot.data[which(
  biplot.data$Size == "Oncaeid" | biplot.data$Size == "Oithonid"  
  ),]$Clade <- "Particle Feeder"
biplot.data[which(
  biplot.data$Size == "Metridia" | biplot.data$Size == "Pleuromamma" | biplot.data$Size == "Harpactacoid"
  ),]$Clade <- "Vertical Migrator"

biplot.data <-
  subset(biplot.data, !is.na(Clade))


ggplot(
  data = subset(biplot.data),
  aes(x = Surface, xmax = SurfaceMax, xmin = SurfaceMin,
      y = FWL, ymax = FWLMax, ymin = FWLMin,
      color = Clade, fill = Clade)
  ) +
  geom_point() +
  stat_ellipse(type = "t", level = 0.95, geom = "polygon", alpha = 0.2) +
  labs(color = "Feeding Clade", fill = "Feeding Clade")

```

# Corrected $\dNSAA$ profiles {-}

Let's also try plotting depth profiles of the average $\dN$ values of all SAAs (Ser, Gly, Phe, Lys) after being corrected for trophic discrimination, alongside those of traps and particles.

```{r SAA-depth_profiles, warning=FALSE, dpi=300, fig.width=8.5, fig.height=5}

sizes <- c("0.06-0.2 mm", "0.2-0.5 mm", "1-2 mm", "2-5 mm", ">5 mm",
           "Oithonid", "Harpactacoid", "Pleuromamma", "Peuromamma", "Ostracod", "Oncaeid", "Gaussia", "Chaetognath","Radiolarian", "Metridia", "Neocalanus","Gaetanus")
variables.temp <- colnames(posts$base$mode)[1:9]
base.mode <- 
  subset(
  bind_rows(
    posts.5N$base$mode,
    posts.8N$base$mode,
    posts.ALOHAS$base$mode,
    posts.ALOHAW$base$mode,
    posts.OSP$base$mode,
    posts.PAP$base$mode),
  Size != "0.06-0.2 mm")# & Location == i)
base.mode$SAA <- rowMeans(cbind(base.mode$d15NSer, base.mode$d15NGly, base.mode$d15NPhe, base.mode$d15NLys), na.rm = TRUE)
base.mode.long <-
  melt(base.mode,
       id.vars = c(variables.temp),
       variable.name = "AA",
       value.name = "d15N")
base.mode.long$Size <- factor(base.mode.long$Size, levels = sizes)
base.HDI95 <- 
  subset(
    bind_rows(
    posts.5N$base$HDI95,
    posts.8N$base$HDI95,
    posts.ALOHAS$base$HDI95,
    posts.ALOHAW$base$HDI95,
    posts.OSP$base$HDI95,
    posts.PAP$base$HDI95),
  Size != "0.06-0.2 mm")# & Location == i)
base.HDI95$SAA <- rowMeans(cbind(base.HDI95$d15NSer, base.HDI95$d15NGly, base.HDI95$d15NPhe, base.HDI95$d15NLys), na.rm = TRUE)
base.HDI95.long <-
  melt(base.HDI95,
       id.vars = c(variables.temp),
       variable.name = "AA",
       value.name = "d15N")
base.HDI95.long$Size <- factor(base.HDI95.long$Size, levels = sizes)
base.HDI90 <- 
  subset(
    bind_rows(
    posts.5N$base$HDI90,
    posts.8N$base$HDI90,
    posts.ALOHAS$base$HDI90,
    posts.ALOHAW$base$HDI90,
    posts.OSP$base$HDI90,
    posts.PAP$base$HDI90),
  Size != "0.06-0.2 mm")# & Location == i)
base.HDI90$SAA <- rowMeans(cbind(base.HDI90$d15NSer, base.HDI90$d15NGly, base.HDI90$d15NPhe, base.HDI90$d15NLys), na.rm = TRUE)
base.HDI90.long <-
  melt(base.HDI90,
       id.vars = c(variables.temp),
       variable.name = "AA",
       value.name = "d15N")
base.HDI90.long$Size <- factor(base.HDI90.long$Size, levels = sizes)
base.HDI75 <- 
  subset(
    bind_rows(
    posts.5N$base$HDI75,
    posts.8N$base$HDI75,
    posts.ALOHAS$base$HDI75,
    posts.ALOHAW$base$HDI75,
    posts.OSP$base$HDI75,
    posts.PAP$base$HDI75),
  Size != "0.06-0.2 mm")# & Location == i)
base.HDI75$SAA <- rowMeans(cbind(base.HDI75$d15NSer, base.HDI75$d15NGly, base.HDI75$d15NPhe, base.HDI75$d15NLys), na.rm = TRUE)
base.HDI75.long <-
  melt(base.HDI75,
       id.vars = c(variables.temp),
       variable.name = "AA",
       value.name = "d15N")
base.HDI75.long$Size <- factor(base.HDI75.long$Size, levels = sizes)
base.HDI50 <- 
  subset(
    bind_rows(
    posts.5N$base$HDI50,
    posts.8N$base$HDI50,
    posts.ALOHAS$base$HDI50,
    posts.ALOHAW$base$HDI50,
    posts.OSP$base$HDI50,
    posts.PAP$base$HDI50),
  Size != "0.06-0.2 mm")# & Location == i)
base.HDI50$SAA <- rowMeans(cbind(base.HDI50$d15NSer, base.HDI50$d15NGly, base.HDI50$d15NPhe, base.HDI50$d15NLys), na.rm = TRUE)
base.HDI50.long <-
  melt(base.HDI50,
       id.vars = c(variables.temp),
       variable.name = "AA",
       value.name = "d15N")
base.HDI50.long$Size <- factor(base.HDI50.long$Size, levels = sizes)

# Appending columns with the min and max of the 95% HDI to the mode data frame.
base.mode.long$min95 <- base.HDI95.long$f[seq(1,nrow(base.HDI95.long),2)]
base.mode.long$max95 <- base.HDI95.long$f[seq(2,nrow(base.HDI95.long),2)]

data.all$SAA <- rowMeans(cbind(data.all$d15NSer, data.all$d15NGly, data.all$d15NPhe, data.all$d15NLys), na.rm = TRUE)
    
  data.plots.traps <- subset(data.all, Event == "Trap Deployment")
  data.plots.parts <- subset(data.all, Event == "Pump Cast" & Sizecat != "Surface")
  data.plots.zoops <- subset(base.mode, Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")
  maxdepth <-
    round(max(data.plots.zoops$Depth)+50, -2)
  
  ggplot()+
    geom_smooth( # Particles
      data = data.plots.parts,
      aes(x = SAA, y = Depth, color = Sizecat, fill = Sizecat, group = Sizecat), 
      orientation = "y", level=0.75, span=1.2)+
    geom_point(
      data = data.plots.parts,
      aes(x = SAA, y = Depth, color = Sizecat, fill = Sizecat, group = Sizecat), 
      size=1, shape=21, alpha=0.7)+
    geom_point( # Zooplankton
      data = data.plots.zoops,
      aes(x = SAA, y = Depth, shape = Size),
      color = "black", size = 1.5, stroke = 0.95)+
    # geom_path(
    #   data = data.plots.zoops,
    #   aes(x = SAA, y = Depth, group = Size, inherit = FALSE),
    #   color = "black", size = 1, linetype = "solid", alpha = 0.5)+
    geom_smooth(
      data = data.plots.zoops,
      aes(x = SAA, y = Depth),
      orientation = "y", level=0.95, span=0.9, color = "black", se = FALSE)+
    # geom_errorbarh(
    #   data = data.plots.zoops,
    #   aes(x = SAA, y = Depth, xmin = min95, xmax = max95), 
    #   height = 1, size = 0.5, linetype = 1, color = 'black')+
    geom_point( # Sediment Traps
      data = data.plots.traps,
      aes(x = SAA, y = Depth, color = Sizecat, fill = Sizecat),
      size = 1.5, stroke = 0.75, shape = 6)+
    # geom_errorbarh(
    #   data = data.plots.traps,
    #   aes(x = SAA, y = Depth, xmin = min95, xmax = max95), 
    #   height = 1, size = 0.5, linetype = 1, color = 'black')+
    scale_y_reverse() + ylab('Depth (m)') +
    scale_x_continuous(minor_breaks = seq(-8,16,2), breaks = seq(-8,16,4))+ 
    xlab(expression(delta^{15}*"N"[SAA]*" (\u2030)")) + 
    labs(color = "Particles", fill="Particles", shape = "Zooplankton")+
    theme_light()+theme(strip.text.x = element_text(size = 8))+ 
    coord_cartesian(expand = FALSE, ylim = c(maxdepth,0))+
    facet_wrap(~ interaction(Location), nrow = 2, scales = "free", dir="v")+
    scale_color_discrete(type = c("#F8766D", "#00BA38", "#619CFF","black"))+
    scale_fill_discrete(type = c("#F8766D", "#00BA38", "#619CFF","white"))
# }

```

# Are trophic parameters related to f(surface)? {-}

```{r trophic-vs-f, dpi = 300, fig.width = 5, fig.asp = 0.6}
trophic.mode <- 
  bind_rows(
    posts.5N$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.8N$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAS$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAW$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.OSP$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.PAP$trophic$mode[c(variables,"PTS","MTS","FWL")])
  # Size != "0.06-0.2 mm")
trophic.mode$baseTP <- (base.mode$d15NAla - base.mode$d15NPhe - 3.2) / 6.3 + 1
trophic.mode <- 
  subset(trophic.mode, Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")

f.mode <-
  subset(
  bind_rows(
    posts.5N$f$mode[c(variables,"Surface","Large","Small")],
    posts.8N$f$mode[c(variables,"Surface","Large","Small")],
    posts.ALOHAS$f$mode[c(variables,"Surface","Large","Small")],
    posts.ALOHAW$f$mode[c(variables,"Surface","Large","Small")],
    posts.OSP$f$mode[c(variables,"Surface","Large","Small")],
    posts.PAP$f$mode[c(variables,"Surface","Large","Small")]),
  # Size != "0.06-0.2 mm")
  Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm")

posterior.modes <- cbind(trophic.mode, f.mode[c("Surface","Large","Small")])

ggplot(
  data = subset(posterior.modes, Depth > 200),
  aes(x = Surface, y = FWL, color = -Depth, fill = -Depth))+
  geom_smooth(
    method = "lm", se = FALSE, lty = 2)+
  geom_smooth(
    method = "lm", se = TRUE, color = "black", fill = "grey50")+
  geom_point(
    size = 3, shape = 21, color = "black")

LM <- lm(
  FWL ~ Surface + Depth,
  data = posterior.modes)
summary(LM)
anova(LM)
plot(allEffects(LM))

ggplot(
  data = subset(posterior.modes, Depth > 200),
  aes(x = Surface, y = baseTP, color = -Depth, fill = -Depth))+
  geom_smooth(
    method = "lm", se = FALSE, lty = 2)+
  geom_smooth(
    method = "lm", se = TRUE, color = "black", fill = "grey50")+
  geom_point(
    size = 3, shape = 21, color = "black")
```


# Comparison with oceanographic parameters - all samples {-}

Now that we've established values for mixing coefficients and trophic coefficients for zooplankton across these various locations, we'd like to examine some potential basin-scale trends in these parameters. Here are the variables we think might reasonably predict the importance of different organic matter sources to the food web.

**Depth: ** distance from the surface should influence the importance of surface organic matter to the food web. We also might expect that smaller particles might become a more important food source at depth, though this might not be a linear effect.

**NPP: ** The amount of NPP occurring in a given location should dictate the amount of sinking material available to MPZ communities. On the other hand, more NPP is also generally correlateed with more DVM.

**EXPORT: ** The amount of POM leaving the euphotic zone should also impact thee importance of sinking particles to the MPZ community.

**DVM Biomass: ** The quantity of animals doing DVM should directly influence the availability of surface POM to the MPZ community.

**Export Ratio: ** The ratio of NPP to EXPORT is related to how efficiently the EZ community consumes primary production. A low export ratio would indicate high NPP with low export, which should favor DVM as a strategy for bringing carbon to depth. A high export ratio should favor a sit and wait strategy of consuming sinking POM within the MPZ.

Let's do some quick regressions to assess these hypotheses. Of course, this exercise has been done before by Romero-romero et al. (2020). We are simply repeating it with revised mixing model results.

Since we are essentially regressing compositional data, a binomial or quasibinomial distribution would probably be best.

```{r}
data.romero <- as.data.frame(read_excel("Data/Romero-Romero2020.xlsx", sheet = "Romero-Romero2020(wPAP)" ))

f.mode <- 
  subset(
    bind_rows(
    posts.5N$f$mode[c(variables,"Surface","Large","Small")],
    posts.8N$f$mode[c(variables,"Surface","Large","Small")],
    posts.ALOHAS$f$mode[c(variables,"Surface","Large","Small")],
    posts.ALOHAW$f$mode[c(variables,"Surface","Large","Small")],
    posts.OSP$f$mode[c(variables,"Surface","Large","Small")],
    posts.PAP$f$mode[c(variables,"Surface","Large","Small")]),
    Size == "0.2-0.5 mm" | Size == "1-2 mm" | Size == "2-5 mm" | Size == ">5 mm"
    # Size == "0.2-0.5 mm" | 
    # Size == "1-2 mm"
    )

# WORKING ON POOLING SIZE CLASSES WITHIN EACH DEPTH AT EACH LOCATION
f.mode.pooled <- aggregate(
  x = cbind(Surface, Large, Small) ~ Location + Epoch + Event + Depth + Type,
  data = f.mode,
  FUN = mean
  )


trophic.mode <- 
  subset(
  bind_rows(
    posts.5N$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.8N$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAS$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.ALOHAW$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.OSP$trophic$mode[c(variables,"PTS","MTS","FWL")],
    posts.PAP$trophic$mode[c(variables,"PTS","MTS","FWL")]),
  Size != "0.06-0.2 mm")# & Location == i)
# Let's calculate TP at the base of the food web
base.mode <- 
  subset(
  bind_rows(
    posts.5N$base$mode[c(variables,"d15NAla","d15NPhe")],
    posts.8N$base$mode[c(variables,"d15NAla","d15NPhe")],
    posts.ALOHAS$base$mode[c(variables,"d15NAla","d15NPhe")],
    posts.ALOHAW$base$mode[c(variables,"d15NAla","d15NPhe")],
    posts.OSP$base$mode[c(variables,"d15NAla","d15NPhe")],
    posts.PAP$base$mode[c(variables,"d15NAla","d15NPhe")]),
  Size != "0.06-0.2 mm")# & Location == i)
trophic.mode$baseTP <- (base.mode$d15NAla - base.mode$d15NPhe - 3.2) / 6.3 + 1
trophic.mode$Size <- factor(trophic.mode$Size, levels = sizes)

trophic.mode.mean <- aggregate(
  x = cbind(FWL,baseTP) ~ Depth + Location,
  data = subset(trophic.mode,
                Size == "0.2-0.5 mm" | Size == "1-2 mm" | 
                  Size == "2-5 mm" | Size == ">5 mm"),
  FUN = "mean"
)
```

## Depth {-}

We'll look at trends across depth at each location. Looking at the depth profile above, we see that if there is a depth dependence in mixing coefficients its is probably non-linear. We'll start, then, by taking the square root transform of depth.

First we will do this on all the data across all locations.

```{r Depth, fig.width=8, fig.asp=0.4}

print("===== SURFACE =====")
plot1 <- ggplot(
  data = f.mode.pooled,
  aes(x = Depth, y = Surface, color = Location, fill = Location))+
  geom_smooth(
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2, color = "black", fill = "grey50")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  ggtitle("Surface")
MOD1 <- glm(Surface ~ Depth,
         data = f.mode.pooled,
         family = quasibinomial())
print("----- SUMMARY -----")
summary(MOD1)
print("----- ANOVA -----")
anova(MOD1)
# plot(allEffects(MOD1))

print("===== LARGE =====")
plot2 <- ggplot(
  data = f.mode.pooled,
  aes(x = Depth, y = Large, color = Location, fill = Location))+
  geom_smooth(
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2, color = "black", fill = "grey50")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  ggtitle("Large")
MOD2 <- glm(Large ~ Depth,
         data = f.mode.pooled,
         family = quasibinomial()
)
print("----- SUMMARY -----")
summary(MOD2)
print("----- ANOVA -----")
anova(MOD2)
# plot(allEffects(MOD2))

print("===== SMALL =====")
plot3 <- ggplot(
  data = f.mode.pooled,
  aes(x = Depth, y = Small, color = Location, fill = Location))+
  geom_smooth(
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2, color = "black", fill = "grey50")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  ggtitle("Small")
MOD3 <- glm(Small ~ Depth,
         data = f.mode.pooled,
         family = quasibinomial()
)
print("----- SUMMARY -----")
summary(MOD3)
print("----- ANOVA -----")
anova(MOD3)
# plot(allEffects(MOD3))

ggarrange(
  plot1, plot2, plot3,
  nrow = 1, common.legend = TRUE, legend = "bottom"
)
```

There appears to be a statistically significant relationship between f(surface) and Depth. This is true for the aggregated data (p = `r anova(MOD1)[2,6]`), but the fit is poor because of high values for f(surface) at deeper depths at ALOHA. There is also true for f(small) (p = `r anova(MOD3)[2,6]`)

Now we'll specify location as a second predictor.

```{r Depth-Location, fig.width=8, fig.height=6, eval=FALSE}

print("===== SURFACE =====")

plot1 <- ggplot(
  data = f.mode,
  aes(x = Depth, y = Surface, color = Size, fill = Size))+
  geom_smooth(
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2)+
  geom_point(
    size = 3, shape = 21, color = "black")+
  facet_wrap(~ Location, nrow=1)+
  ylim(0,1)+
  ggtitle("Surface")
MOD1 <- glm(Surface ~ Depth + Location + Size,
         data = f.mode,
         family = quasibinomial())
print("----- SUMMARY -----")
summary(MOD1)
print("----- ANOVA -----")
anova(MOD1)
plot(allEffects(MOD1))

print("===== LARGE =====")
plot2 <- ggplot(
  data = f.mode,
  aes(x = Depth, y = Large, color = Size, fill = Size))+
  geom_smooth(
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2)+
  geom_point(
    size = 3, shape = 21, color = "black")+
  facet_wrap(~ Location, nrow=1)+
  ylim(0,1)+
  ggtitle("Large")
MOD2 <- glm(Large ~ Depth + Location + Size,
         data = f.mode,
         family = quasibinomial())
print("----- SUMMARY -----")
summary(MOD2)
print("----- ANOVA -----")
anova(MOD2)
plot(allEffects(MOD2))

print("===== SMALL =====")
plot3 <- ggplot(
  data = f.mode,
  aes(x = Depth, y = Small, color = Size, fill = Size))+
  geom_smooth(
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2)+
  geom_point(
    size = 3, shape = 21, color = "black")+
  facet_wrap(~ Location, nrow=1)+
  ylim(0,1)+
  ggtitle("Small")
MOD3 <- glm(Small ~ Depth + Location + Size,
         data = f.mode,
         family = quasibinomial())
print("----- SUMMARY -----")
summary(MOD3)
print("----- ANOVA -----")
anova(MOD3)
plot(allEffects(MOD3))

ggarrange(
  plot1, plot2, plot3,
  nrow = 3, common.legend = TRUE, legend = "bottom"
)
```

The fit with f(surface) is much stronger when location is included as a predictor in the model (p = `r anova(MOD1)[2,6]`). Location is a also a significant predictor (p = `r anova(MOD1)[3,6]`).

This suggests that in general surface particles become less important at deeper depths, but that the nature of this relationship is location specific. Let's figure out what is driving these trends across space by looking using site-specific oceanographic variables as predictors. We will need to include depth as a predictor in these models as well, though we may choose to do this by just subsetting the data within specific depth bins.

## NPP {-}

```{r incorportating-NPP-data}
locs <- unique(f.mode$Location)
for (i in locs) {
  f.mode$NPP[which(f.mode$Location == i)] <- 
    data.romero$`NPP (best)`[which(data.romero$Site == i)]
}
locs <- unique(f.mode.pooled$Location)
f.mode.pooled$NPP <- NA
for (i in locs) {
  f.mode.pooled$NPP[which(f.mode.pooled$Location == i)] <-
    data.romero$`NPP (best)`[which(data.romero$Site == i)]
}

locs <- unique(f.mode.pooled$Location)
trophic.mode.mean$NPP <- NA
for (i in locs) {
  trophic.mode.mean$NPP[which(trophic.mode.mean$Location == i)] <-
    data.romero$`NPP (best)`[which(data.romero$Site == i)]
}
```

First we'll try just doing a glm with NPP as a predictor for f(surface).

```{r NPP, fig.width=8, fig.asp=0.4}

print("===== SURFACE =====")

plot1 <- ggplot(
  data = f.mode.pooled,
  aes(x = NPP, y = Surface, color = Location, fill = Location))+
  geom_smooth(
    data = subset(f.mode.pooled, Location != "PAP"),
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, color = "black", fill="grey")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  ylim(0,1)+
  ggtitle("Surface")
MOD1 <- glm(Surface ~ NPP,
         data = f.mode,
         family = quasibinomial())
print("----- SUMMARY -----")
summary(MOD1)
print("----- ANOVA -----")
anova(MOD1)
# plot(allEffects(MOD1))

print("===== LARGE =====")
plot2 <- ggplot(
  data = f.mode.pooled,
  aes(x = NPP, y = Large, color = Location, fill = Location))+
  geom_smooth(
    data = subset(f.mode.pooled, Location != "PAP"),
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, color = "black", fill="grey")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  ylim(0,1)+
  ggtitle("Large")
MOD2 <- glm(Large ~ NPP,
         data = f.mode,
         family = quasibinomial())
print("----- SUMMARY -----")
summary(MOD2)
print("----- ANOVA -----")
anova(MOD2)
# plot(allEffects(MOD2))

print("===== SMALL =====")
plot3 <- ggplot(
  data = f.mode.pooled,
  aes(x = NPP, y = Small, color = Location, fill = Location))+
  geom_smooth(
    data = subset(f.mode.pooled, Location != "PAP"),
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, color = "black", fill="grey")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  ylim(0,1)+
  ggtitle("Small")
MOD3 <- glm(Small ~ NPP,
         data = f.mode,
         family = quasibinomial())
print("----- SUMMARY -----")
summary(MOD3)
print("----- ANOVA -----")
anova(MOD3)
# plot(allEffects(MOD3))

ggarrange(
  plot1, plot2, plot3,
  nrow = 1, common.legend = TRUE, legend = "bottom"
)

```

We also want to look and see if FWL or TP at the base of the foodweb are related to NPP.

```{r NPP-trophic, fig.width=5, fig.height=3, dpi=300}

ggarrange(

ggplot(
  data = subset(trophic.mode.mean, Depth>200),
  aes(x = NPP, y = baseTP, color = Location, fill = Location))+
  geom_smooth(
    data = subset(trophic.mode.mean),
    method = "lm", formula = y ~ poly(x, 2),
    se = TRUE, color = "black", fill="grey", )+
  geom_point(
    size = 3, shape = 21, color = "black")+
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank())+
  ylim(1,2.5)
  ,

ggplot(
  data = subset(trophic.mode.mean, Depth>200),
  aes(x = NPP, y = FWL, color = Location, fill = Location))+
  geom_line(
    data = trophic.HDI95.long,
    aes(x = value, y = Depth, color = Size, group = interaction(Depth, Size)),
    alpha = 0.5, size = 1,
    position = position_dodgev(height = 100))+
  geom_line(
    data = trophic.HDI90.long,
    aes(x = value, y = Depth, color = Size, group = interaction(Depth, Size)),
    alpha = 0.7, size = 1.5,
    position = position_dodgev(height = 100))+
  geom_line(
    data = trophic.HDI75.long,
    aes(x = value, y = Depth, color = Size, group = interaction(Depth, Size)),
    alpha = 1, size = 2,
    position = position_dodgev(height = 100))+
  geom_line(
    data = trophic.HDI50.long,
    aes(x = value, y = Depth, color = Size, group = interaction(Depth, Size)),
    alpha = 1, size = 3,
    position = position_dodgev(height = 100))+
  geom_smooth(
    data = subset(trophic.mode.mean),
    method = "lm", formula = y ~ poly(x, 2),
    se = TRUE, color = "black", fill="grey", )+
  geom_point(
    size = 3, shape = 21, color = "black")+
  ylim(1,2.5),

nrow = 2,
heights = c(1,1.2),
legend = "right",
common.legend = TRUE
)

```

This is showing that NPP is a significant predictor of f(surface) (p = `r anova(MOD1)[2,6]`), f(large) (p = `r anova(MOD2)[2,6]`), and f(small) (p = `r anova(MOD3)[2,6]`). 

We know depth is a significant predictor so lets also include that in the GLM. We would include size, but we dont have enough representation of some sizes across sites so it doesn't come out as being significant.

```{r NPP-Depth, fig.width=8, fig.height=4}

MOD1 <- glm(Surface ~ NPP + Depth,
         data = f.mode,
         family = quasibinomial())
print("----- SUMMARY -----")
summary(MOD1)
print("----- ANOVA -----")
anova(MOD1)
plot(allEffects(MOD1))

print("===== LARGE =====")

MOD2 <- glm(Large ~ NPP + Depth,
         data = f.mode,
         family = quasibinomial())
print("----- SUMMARY -----")
summary(MOD2)
print("----- ANOVA -----")
anova(MOD2)
plot(allEffects(MOD2))

print("===== SMALL =====")
MOD3 <- glm(Small ~ NPP + Depth,
         data = f.mode,
         family = quasibinomial())
print("----- SUMMARY -----")
summary(MOD3)
print("----- ANOVA -----")
anova(MOD3)
plot(allEffects(MOD3))
```

NPP continues to be a significant predictor of f(surface) (p = `r anova(MOD1)[2,6]`), f(large) (p = `r anova(MOD2)[2,6]`), and f(small) (p = `r anova(MOD3)[2,6]`). 

It's hard to to plot that effect, and we may more interested in these relationships within specific depth strata, so let's make some plots just looking at the EZ (0-100 m), the upper MPZ (200-700 m), the lower MPZ (700-1500 m).

```{r DepthStrata-NPP, fig.width=8, fig.height=6, warning=FALSE}

f.mode$Strata <- factor("EZ", 
                        levels = c("EZ","MPZ upper","MPZ lower","Bathyl"))
f.mode$Strata[which(f.mode$Depth > 100)] <- "MPZ upper"
f.mode$Strata[which(f.mode$Depth > 700)] <- "MPZ lower"
# f.mode$Strata[which(f.mode$Depth > 1000)] <- "Bathyl"

f.mode.pooled$Strata <- factor("EZ", 
                        levels = c("EZ","MPZ upper","MPZ lower","Bathyl"))
f.mode.pooled$Strata[which(f.mode.pooled$Depth > 100)] <- "MPZ upper"
f.mode.pooled$Strata[which(f.mode.pooled$Depth > 700)] <- "MPZ lower"
# f.mode.pooled$Strata[which(f.mode.pooled$Depth > 1000)] <- "Bathyl"

print("===== SURFACE =====")

plot1 <- ggplot(
  data = f.mode.pooled,
  aes(x = NPP, y = Surface, color = Location, fill = Location))+
  geom_smooth(
    data = subset(f.mode.pooled, Location != "PAP"),
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2, color = "black", fill = "black")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  facet_wrap(~ Strata, nrow = 3)+
  ylim(0,1)+
  ggtitle("Surface")
MOD1 <- glm(Surface ~ Depth + NPP,
         data = f.mode.pooled,
         family = quasibinomial())
print("----- SUMMARY -----")
summary(MOD1)
print("----- ANOVA -----")
anova(MOD1)
# plot(allEffects(MOD1))

print("===== LARGE =====")
plot2 <- ggplot(
  data = f.mode.pooled,
  aes(x = NPP, y = Large, color = Location, fill = Location))+
  geom_smooth(
    data = subset(f.mode.pooled, Location != "PAP"),
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2, color = "black", fill = "black")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  facet_wrap(~ Strata, nrow = 3)+
  ylim(0,1)+
  ggtitle("Large")
MOD2 <- glm(Large ~ Depth + NPP,
         data = f.mode.pooled,
         family = quasibinomial())
print("----- SUMMARY -----")
summary(MOD2)
print("----- ANOVA -----")
anova(MOD2)
# plot(allEffects(MOD2))

print("===== SMALL =====")
plot3 <- ggplot(
  data = f.mode.pooled,
  aes(x = NPP, y = Small, color = Location, fill = Location))+
  geom_smooth(
    data = subset(f.mode.pooled, Location != "PAP"),
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2, color = "black", fill = "black")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  facet_wrap(~ Strata, nrow = 3)+
  ylim(0,1)+
  ggtitle("Small")
MOD3 <- glm(Small ~ Depth + NPP,
         data = f.mode.pooled,
         family = quasibinomial())
print("----- SUMMARY -----")
summary(MOD3)
print("----- ANOVA -----")
anova(MOD3)
# plot(allEffects(MOD3))

ggarrange(
  plot1, plot2, plot3,
  nrow = 1, common.legend = TRUE, legend = "bottom"
)
```

Looking at the data this way we can see that the relationship with NPP is only strong within certain depth strata. Let's continue on to examine other predictors.

## Export {-}

Next we will look at particle export at the base of the euphotic zone. We define the base of the EZ here as the depth at which chl is 1% of its maximum. Export is estimated from Th-234 disequillibrium.

```{r incorportating-Export-data}
locs <- unique(f.mode$Location)
f.mode$Export <- as.numeric(NA)
for (i in locs) {
  f.mode$Export[which(f.mode$Location == i)] <- 
    as.numeric(data.romero$fluxC.PPZ.avg[which(data.romero$Site == i)])
}
locs <- unique(f.mode.pooled$Location)
f.mode.pooled$Export <- as.numeric(NA)
for (i in locs) {
  f.mode.pooled$Export[which(f.mode.pooled$Location == i)] <- 
    as.numeric(data.romero$fluxC.PPZ.avg[which(data.romero$Site == i)])
}
```

At this point we've established that location is an important secondary predictor to include. We will choose to implment depth strata as a discrete secondary predictor in regressions going forward.

```{r DepthStrata-Export, fig.width=8, fig.height=6, warning=FALSE}

f.mode$Strata <- factor("EZ", 
                        levels = c("EZ","MPZ upper","MPZ lower","Bathyl"))
f.mode$Strata[which(f.mode$Depth > 100)] <- "MPZ upper"
f.mode$Strata[which(f.mode$Depth > 700)] <- "MPZ lower"
# f.mode$Strata[which(f.mode$Depth > 1000)] <- "Bathyl"
f.mode.pooled$Strata <- factor("EZ", 
                        levels = c("EZ","MPZ upper","MPZ lower","Bathyl"))
f.mode.pooled$Strata[which(f.mode.pooled$Depth > 100)] <- "MPZ upper"
f.mode.pooled$Strata[which(f.mode.pooled$Depth > 700)] <- "MPZ lower"
# f.mode.pooled$Strata[which(f.mode.pooled$Depth > 1000)] <- "Bathyl"

print("===== SURFACE =====")

plot1 <- ggplot(
  data = f.mode.pooled,
  aes(x = Export, y = Surface, color = Location, fill = Location))+
  geom_smooth(
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2, color = "black", fill = "black")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  facet_wrap(~ Strata, nrow = 3)+
  ylim(0,1)+
  ggtitle("Surface")
MOD1 <- glm(Surface ~ Depth + Export,
         data = f.mode,
         family = quasibinomial())
print("----- SUMMARY -----")
summary(MOD1)
print("----- ANOVA -----")
anova(MOD1)
# plot(allEffects(MOD1))

print("===== LARGE =====")
plot2 <- ggplot(
  data = f.mode.pooled,
  aes(x = Export, y = Large, color = Location, fill = Location))+
  geom_smooth(
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2, color = "black", fill = "black")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  facet_wrap(~ Strata, nrow = 3)+
  ylim(0,1)+
  ggtitle("Large")
MOD2 <- glm(Large ~ Depth + Export,
         data = f.mode,
         family = quasibinomial())
print("----- SUMMARY -----")
summary(MOD2)
print("----- ANOVA -----")
anova(MOD2)
# plot(allEffects(MOD2))

print("===== SMALL =====")
plot3 <- ggplot(
  data = f.mode.pooled,
  aes(x = Export, y = Small, color = Location, fill = Location))+
  geom_smooth(
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2, color = "black", fill = "black")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  facet_wrap(~ Strata, nrow = 3)+
  ylim(0,1)+
  ggtitle("Small")
MOD3 <- glm(Small ~ Depth + Export,
         data = f.mode,
         family = quasibinomial())
print("----- SUMMARY -----")
summary(MOD3)
print("----- ANOVA -----")
anova(MOD3)
# plot(allEffects(MOD3))

ggarrange(
  plot1, plot2, plot3,
  nrow = 1, common.legend = TRUE, legend = "bottom"
)
```

While anova does not identify C export flux as a significant predictor of f(surface) (p = `r anova(MOD1)[3,6]`), this is because a relationship is only observed in bathyl samples. Let's re-run this for bathyl samples alone.

```{r bathyl-Export, fig.width=8, fig.height=3, warning=FALSE}

print("===== SURFACE =====")

plot1 <- ggplot(
  data = subset(f.mode, Strata == "MPZ lower"),
  aes(x = Export, y = Surface, color = Location, fill = Location, group = Strata))+
  geom_smooth(
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2, color = "black", fill = "black")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  facet_wrap(~ Strata, nrow = 2)+
  ylim(0,1)+
  ggtitle("Surface")
MOD1 <- glm(Surface ~ Export,
         data = subset(f.mode, Strata == "MPZ lower"),
         family = quasibinomial())
print("----- SUMMARY -----")
summary(MOD1)
print("----- ANOVA -----")
anova(MOD1)
# plot(allEffects(MOD1))

print("===== LARGE =====")
plot2 <- ggplot(
  data = subset(f.mode, Strata == "MPZ lower"),
  aes(x = Export, y = Large, color = Location, fill = Location, group = Strata))+
  geom_smooth(
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2, color = "black", fill = "black")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  facet_wrap(~ Strata, nrow = 2)+
  ylim(0,1)+
  ggtitle("Large")
MOD2 <- glm(Large ~ Export,
         data = subset(f.mode, Strata == "MPZ lower"),
         family = quasibinomial())
print("----- SUMMARY -----")
summary(MOD2)
print("----- ANOVA -----")
anova(MOD2)
# plot(allEffects(MOD2))

print("===== SMALL =====")
plot3 <- ggplot(
  data = subset(f.mode, Strata == "MPZ lower"),
  aes(x = Export, y = Small, color = Location, fill = Location, group = Strata))+
  geom_smooth(
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2, color = "black", fill = "black")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  facet_wrap(~ Strata, nrow = 2)+
  ylim(0,1)+
  ggtitle("Small")
MOD3 <- glm(Small ~ Export,
         data = subset(f.mode, Strata == "MPZ lower"),
         family = quasibinomial())
print("----- SUMMARY -----")
summary(MOD3)
print("----- ANOVA -----")
anova(MOD3)
# plot(allEffects(MOD3))

ggarrange(
  plot1, plot2, plot3,
  nrow = 1, common.legend = TRUE, legend = "bottom"
)
```

Just looking at bathyl samples, anova now indicates a significant relationship between f(surface) and export. Yet we do note a pattern across all three sources, where surface particles are important when flux is high, large when flux is intermediate, and small when flux is low. This is essentially an extension of the principal finding of Romero-romero et al. (2020).

## Export Ratio {-}

Before we move on to look at DVM biomass, we'll quickly look at the export ratio. This is just export flux / NPP.

```{r incorportating-ExportRatio-data}
locs <- unique(f.mode$Location)
f.mode$ExportRatio <- f.mode$Export / f.mode$NPP

locs <- unique(f.mode.pooled$Location)
f.mode.pooled$ExportRatio <- f.mode.pooled$Export / f.mode.pooled$NPP
```


```{r DepthStrata-ExportRatio, fig.width=8, fig.height=6, warning=FALSE}

f.mode$Strata <- factor("EZ", 
                        levels = c("EZ","MPZ upper","MPZ lower","Bathyl"))
f.mode$Strata[which(f.mode$Depth > 100)] <- "MPZ upper"
f.mode$Strata[which(f.mode$Depth > 700)] <- "MPZ lower"
# f.mode$Strata[which(f.mode$Depth > 1000)] <- "Bathyl"

f.mode.pooled$Strata <- factor("EZ", 
                        levels = c("EZ","MPZ upper","MPZ lower","Bathyl"))
f.mode.pooled$Strata[which(f.mode.pooled$Depth > 100)] <- "MPZ upper"
f.mode.pooled$Strata[which(f.mode.pooled$Depth > 700)] <- "MPZ lower"
# f.mode.pooled$Strata[which(f.mode.pooled$Depth > 1000)] <- "Bathyl"

print("===== SURFACE =====")

plot1 <- ggplot(
  data = f.mode.pooled,
  aes(x = ExportRatio, y = Surface, color = Location, fill = Location))+
  geom_smooth(
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2, color = "black", fill = "black")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  facet_wrap(~ Strata, nrow = 3)+
  ylim(0,1)+
  ggtitle("Surface")
MOD1 <- glm(Surface ~ Depth + ExportRatio,
         data = f.mode,
         family = quasibinomial())
print("----- SUMMARY -----")
summary(MOD1)
print("----- ANOVA -----")
anova(MOD1)
# plot(allEffects(MOD1))

print("===== LARGE =====")
plot2 <- ggplot(
  data = f.mode.pooled,
  aes(x = ExportRatio, y = Large, color = Location, fill = Location))+
  geom_smooth(
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2, color = "black", fill = "black")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  facet_wrap(~ Strata, nrow = 3)+
  ylim(0,1)+
  ggtitle("Large")
MOD2 <- glm(Large ~ Depth + ExportRatio,
         data = f.mode,
         family = quasibinomial())
print("----- SUMMARY -----")
summary(MOD2)
print("----- ANOVA -----")
anova(MOD2)
# plot(allEffects(MOD2))

print("===== SMALL =====")
plot3 <- ggplot(
  data = f.mode.pooled,
  aes(x = ExportRatio, y = Small, color = Location, fill = Location))+
  geom_smooth(
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2, color = "black", fill = "black")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  facet_wrap(~ Strata, nrow = 3)+
  ylim(0,1)+
  ggtitle("Small")
MOD3 <- glm(Small ~ Depth + ExportRatio,
         data = f.mode,
         family = quasibinomial())
print("----- SUMMARY -----")
summary(MOD3)
print("----- ANOVA -----")
anova(MOD3)
# plot(allEffects(MOD3))

ggarrange(
  plot1, plot2, plot3,
  nrow = 1, common.legend = TRUE, legend = "bottom"
)
```

Export ratio turns out to be a pretty decent predictor of f(surface) (p = `r anova(MOD1)[3,6]`) and f(large) (p = `r anova(MOD2)[3,6]`), but not of f(small) (p = `r anova(MOD3)[3,6]`). 

## Diel Vertical Migrator Biomass {-}

The last predictor we will consider is DVM biomass. This is a depth specific metric, like carbon export. Again, we will use a dynamic depth cutoff defined by the base of the PPZ.

```{r incorportating-DVM-data}
locs <- unique(f.mode$Location)
f.mode$DVM <- NA
for (i in locs) {
  f.mode$DVM[which(f.mode$Location == i)] <- 
    as.numeric(data.romero$migbio.PPZ[which(data.romero$Site == i)])
}
f.mode$DVMProp <- NA
for (i in locs) {
  f.mode$DVMProp[which(f.mode$Location == i)] <- 
    as.numeric(data.romero$prop.migbio.200[which(data.romero$Site == i)])
}
locs <- unique(f.mode.pooled$Location)
f.mode.pooled$DVM <- NA
for (i in locs) {
  f.mode.pooled$DVM[which(f.mode.pooled$Location == i)] <- 
    as.numeric(data.romero$migbio.PPZ[which(data.romero$Site == i)])
}
f.mode.pooled$DVMProp <- NA
for (i in locs) {
  f.mode.pooled$DVMProp[which(f.mode.pooled$Location == i)] <- 
    as.numeric(data.romero$prop.migbio.200[which(data.romero$Site == i)])
}
```


```{r DepthStrata-DVM, fig.width=8, fig.height=6, warning=FALSE}

f.mode$Strata <- factor("EZ", 
                        levels = c("EZ","MPZ upper","MPZ lower","Bathyl"))
f.mode$Strata[which(f.mode$Depth > 100)] <- "MPZ upper"
f.mode$Strata[which(f.mode$Depth > 700)] <- "MPZ lower"
# f.mode$Strata[which(f.mode$Depth > 1000)] <- "Bathyl"

f.mode.pooled$Strata <- factor("EZ", 
                        levels = c("EZ","MPZ upper","MPZ lower","Bathyl"))
f.mode.pooled$Strata[which(f.mode.pooled$Depth > 100)] <- "MPZ upper"
f.mode.pooled$Strata[which(f.mode.pooled$Depth > 700)] <- "MPZ lower"
# f.mode.pooled$Strata[which(f.mode.pooled$Depth > 1000)] <- "Bathyl"

print("===== SURFACE =====")

plot1 <- ggplot(
  data = f.mode.pooled,
  aes(x = DVM, y = Surface, color = Location, fill = Location))+
  geom_smooth(
    data = subset(f.mode.pooled, Location != "PAP"),
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2, color = "black", fill = "black")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  facet_wrap(~ Strata, nrow = 3)+
  ylim(0,1)+
  ggtitle("Surface")
MOD1 <- glm(Surface ~ Depth + DVM,
         data = f.mode.pooled,
         family = quasibinomial())
print("----- SUMMARY -----")
summary(MOD1)
print("----- ANOVA -----")
anova(MOD1)
# plot(allEffects(MOD1))

print("===== LARGE =====")
plot2 <- ggplot(
  data = f.mode.pooled,
  aes(x = DVM, y = Large, color = Location, fill = Location))+
  geom_smooth(
    data = subset(f.mode.pooled, Location != "PAP"),
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2, color = "black", fill = "black")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  facet_wrap(~ Strata, nrow = 3)+
  ylim(0,1)+
  ggtitle("Large")
MOD2 <- glm(Large ~ Depth + DVM,
         data = f.mode.pooled,
         family = quasibinomial())
print("----- SUMMARY -----")
summary(MOD2)
print("----- ANOVA -----")
anova(MOD2)
# plot(allEffects(MOD2))

print("===== SMALL =====")
plot3 <- ggplot(
  data = f.mode.pooled,
  aes(x = DVM, y = Small, color = Location, fill = Location))+
  geom_smooth(
    data = subset(f.mode.pooled, Location != "PAP"),
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2, color = "black", fill = "black")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  facet_wrap(~ Strata, nrow = 3)+
  ylim(0,1)+
  ggtitle("Small")
MOD3 <- glm(Small ~ Depth + DVM,
         data = f.mode.pooled,
         family = quasibinomial())
print("----- SUMMARY -----")
summary(MOD3)
print("----- ANOVA -----")
anova(MOD3)
# plot(allEffects(MOD3))

ggarrange(
  plot1, plot2, plot3,
  nrow = 1, common.legend = TRUE, legend = "bottom"
)
```

DVM biomass is a signifcant predictor of f(surface) (p = `r anova(MOD1)[3,6]`) and f(small) (p = `r anova(MOD3)[3,6]`), but not of f(large) (p = `r anova(MOD2)[3,6]`). 

## Summary {-}

Let's first review at some basic relationships with NPP.

```{r NPP-relationships, dpi=300, fig.width=5, fig.height=12, warning=FALSE}
ggarrange(

ggplot(
  data = subset(f.mode.pooled, Strata == "EZ"),
  aes(x = NPP, y = Export, color = Location, fill = Location, group = Strata))+
  geom_smooth(
    method = "lm", formula = y ~ poly(x, 2),
    se = TRUE, color = "black", fill="grey")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  coord_cartesian(xlim = c(0,NA), ylim = c(0,NA))+
  theme(axis.title.x = element_blank())+
  xlim(0,80) + ylab(expression("C Export (mmol C/m"^2*"/day)"))+
  scale_fill_discrete(
    labels = c("5° N","8° N","ALOHA S","ALOHA W","Station Papa","N Atlantic")),

ggplot(
  data = subset(f.mode.pooled, Strata == "EZ"),
  aes(x = NPP, y = DVM, color = Location, fill = Location, group = Strata))+
  geom_smooth(
    method = "lm", formula = y ~ x,
    se = TRUE, color = "black", fill="grey")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  coord_cartesian(xlim = c(0,NA), ylim = c(0,NA))+
  theme(axis.title.x = element_blank())+
  xlim(0,80) + ylab(expression("DVM Biomass (mg/m"^2*")")),

ggplot(
  data = subset(trophic.mode.mean, Depth > 200 & Depth < 1000),
  aes(x = NPP, y = baseTP, color = Location, fill = Location))+
  geom_smooth(
    data = subset(trophic.mode.mean),
    method = "lm", formula = y ~ poly(x, 2),
    se = TRUE, color = "black", fill="grey")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  theme(axis.title.x = element_blank())+
  ylim(1,2.5) + xlim(0,80) + ylab("Base TP"),

ggplot(
  data = subset(trophic.mode.mean, Depth > 200 & Depth < 1000),
  aes(x = NPP, y = FWL, color = Location, fill = Location))+
  # geom_line(
  #   data = trophic.HDI95.long,
  #   aes(x = value, y = Depth, color = Size, group = interaction(Depth, Size)),
  #   alpha = 0.5, size = 1,
  #   position = position_dodgev(height = 100))+
  # geom_line(
  #   data = trophic.HDI90.long,
  #   aes(x = value, y = Depth, color = Size, group = interaction(Depth, Size)),
  #   alpha = 0.7, size = 1.5,
  #   position = position_dodgev(height = 100))+
  # geom_line(
  #   data = trophic.HDI75.long,
  #   aes(x = value, y = Depth, color = Size, group = interaction(Depth, Size)),
  #   alpha = 1, size = 2,
  #   position = position_dodgev(height = 100))+
  # geom_line(
  #   data = trophic.HDI50.long,
  #   aes(x = value, y = Depth, color = Size, group = interaction(Depth, Size)),
  #   alpha = 1, size = 3,
  #   position = position_dodgev(height = 100))+
  geom_smooth(
    data = subset(trophic.mode.mean),
    method = "lm", formula = y ~ poly(x, 2),
    se = TRUE, color = "black", fill="grey", )+
  geom_point(
    size = 3, shape = 21, color = "black")+
  theme(axis.title.x = element_blank())+
  ylim(1,2.5) + xlim(0,80) + ylab("Food Web Length"),

ggplot(
  data = subset(f.mode.pooled, Depth > 200 & Depth < 1000),
  aes(x = NPP, y = Surface, color = Location, fill = Location))+
  geom_smooth(
    method = "lm", formula = y ~ poly(x, 2),
    se = TRUE, color = "black", fill="grey", )+
  geom_point(
    size = 3, shape = 21, color = "black")+
  ylim(0,1) + xlim(0,80) + 
  ylab("f(surface)")+
  xlab(expression("NPP (mmol C/"*m^2*"/day)"))+
  scale_y_continuous(
    limits = c(0,1),
    breaks = c(0,0.2,0.4,0.6,0.8,1)),

nrow = 5,
heights = c(1,1,1,1,1.2),
legend = "right",
common.legend = TRUE
)

ggarrange(

ggplot(
  data = subset(f.mode.pooled, Strata == "EZ"),
  aes(x = NPP, y = Export, color = Location, fill = Location, group = Strata))+
  # geom_smooth(
  #   method = "lm", formula = y ~ poly(x, 2),
  #   se = TRUE, color = "black", fill="grey")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  coord_cartesian(xlim = c(0,NA), ylim = c(0,NA))+
  theme(axis.title.x = element_blank())+
  xlim(0,80) + ylab(expression("C Export (mmol C/m"^2*"/day)"))+
  scale_fill_discrete(
    labels = c("5° N","8° N","ALOHA S","ALOHA W","Station Papa","N Atlantic")),

ggplot(
  data = subset(f.mode.pooled, Strata == "EZ"),
  aes(x = NPP, y = DVM, color = Location, fill = Location, group = Strata))+
  # geom_smooth(
  #   method = "lm", formula = y ~ x,
  #   se = TRUE, color = "black", fill="grey")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  coord_cartesian(xlim = c(0,NA), ylim = c(0,NA))+
  theme(axis.title.x = element_blank())+
  xlim(0,80) + ylab(expression("DVM Biomass (mg/m"^2*")")),

ggplot(
  data = subset(trophic.mode.mean, Depth > 200 & Depth < 1000),
  aes(x = NPP, y = baseTP, color = Location, fill = Location))+
  # geom_smooth(
  #   data = subset(trophic.mode.mean),
  #   method = "lm", formula = y ~ poly(x, 2),
  #   se = TRUE, color = "black", fill="grey")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  theme(axis.title.x = element_blank())+
  ylim(1,2.5) + xlim(0,80) + ylab("Base TP"),

ggplot(
  data = subset(trophic.mode.mean, Depth > 200 & Depth < 1000),
  aes(x = NPP, y = FWL, color = Location, fill = Location))+
  # geom_line(
  #   data = trophic.HDI95.long,
  #   aes(x = value, y = Depth, color = Size, group = interaction(Depth, Size)),
  #   alpha = 0.5, size = 1,
  #   position = position_dodgev(height = 100))+
  # geom_line(
  #   data = trophic.HDI90.long,
  #   aes(x = value, y = Depth, color = Size, group = interaction(Depth, Size)),
  #   alpha = 0.7, size = 1.5,
  #   position = position_dodgev(height = 100))+
  # geom_line(
  #   data = trophic.HDI75.long,
  #   aes(x = value, y = Depth, color = Size, group = interaction(Depth, Size)),
  #   alpha = 1, size = 2,
  #   position = position_dodgev(height = 100))+
  # geom_line(
  #   data = trophic.HDI50.long,
  #   aes(x = value, y = Depth, color = Size, group = interaction(Depth, Size)),
  #   alpha = 1, size = 3,
  #   position = position_dodgev(height = 100))+
  # geom_smooth(
  #   data = subset(trophic.mode.mean),
  #   method = "lm", formula = y ~ poly(x, 2),
  #   se = TRUE, color = "black", fill="grey", )+
  geom_point(
    size = 3, shape = 21, color = "black")+
  theme(axis.title.x = element_blank())+
  ylim(1,2.5) + xlim(0,80) + ylab("Food Web Length"),

ggplot(
  data = subset(f.mode.pooled, Depth > 200 & Depth < 1000),
  aes(x = NPP, y = Surface, color = Location, fill = Location))+
  # geom_smooth(
  #   method = "lm", formula = y ~ poly(x, 2),
  #   se = TRUE, color = "black", fill="grey", )+
  geom_point(
    size = 3, shape = 21, color = "black")+
  ylim(0,1) + xlim(0,80) + 
  ylab("f(surface)")+
  xlab(expression("NPP (mmol C/"*m^2*"/day)"))+
  scale_y_continuous(
    limits = c(0,1),
    breaks = c(0,0.2,0.4,0.6,0.8,1)),

nrow = 5,
heights = c(1,1,1,1,1.2),
legend = "right",
common.legend = TRUE
)

#### C Export vs NPP ####
noquote("C Export vs NPP")
LM <- lm(
  data = subset(f.mode.pooled, Strata == "EZ"),
  formula = Export ~ poly(NPP, degree = 2)
)
summary(LM)
anova(LM)

#### DVM vs NPP ####
noquote("DVM vs NPP")
LM <- lm(
  data = subset(f.mode.pooled, Strata == "EZ"),
  formula = DVM ~ NPP
)
summary(LM)
anova(LM)

#### baseTP vs NPP ####
noquote("Base TP vs NPP")
LM <- lm(
  data = subset(trophic.mode.mean, Depth > 200 & Depth < 1000),
  formula = baseTP ~ poly(NPP, degree = 2)
)
summary(LM)
anova(LM)

#### FWL vs NPP ####
noquote("FWL vs NPP")
LM <- lm(
  data = subset(trophic.mode.mean, Depth > 200 & Depth < 1000),
  formula = FWL ~ poly(NPP, degree = 2)
)
summary(LM)
anova(LM)

#### f(surface) vs NPP ####
noquote("f(surface) vs NPP")
LM <- lm(
  data = subset(f.mode.pooled, Depth > 200 & Depth < 1000),
  formula = Surface ~ poly(NPP, degree = 2)
)
summary(LM)
anova(LM)
```

```{r NPP-EXPORToverDVM, dpi=300, fig.width=5, fig.height=3, warning=FALSE}

ggplot(
  data = subset(f.mode.pooled, Strata == "EZ" & Location != "8 N"),
  aes(x = NPP, y = DVM/(Export*12), color = Location, fill = Location, group = Strata))+
  geom_smooth(
    method = "lm", formula = y ~ poly(x, 2),
    se = TRUE, color = "black", fill="grey")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  coord_cartesian(xlim = c(0,NA), ylim = c(0,NA))+
  # theme(axis.title.x = element_blank())+
  xlim(0,80) + ylab(expression("DVM/C Export"))+
  scale_fill_discrete(
    labels = c("5° N","ALOHA S","ALOHA W","Station Papa","N Atlantic"))

ggplot(
  data = subset(f.mode.pooled, Strata == "EZ" & Location != "8 N"),
  aes(x = NPP, y = DVMProp/(Export*12), color = Location, fill = Location, group = Strata))+
  geom_smooth(
    method = "lm", formula = y ~ poly(x, 2),
    se = TRUE, color = "black", fill="grey")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  coord_cartesian(xlim = c(0,NA), ylim = c(0,NA))+
  # theme(axis.title.x = element_blank())+
  xlim(0,80) + ylab(expression("proportion DVM/C Export (mg C)"))+
  scale_fill_discrete(
    labels = c("5° N","ALOHA S","ALOHA W","Station Papa","N Atlantic"))

ggplot(
  data = subset(f.mode.pooled, Strata == "EZ" & Location != "8 N"),
  aes(x = DVM/(Export*12), y = Surface , color = Location, fill = Location, group = Strata))+
  geom_smooth(
    method = "lm", formula = y ~ x,
    se = TRUE, color = "black", fill="grey")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  coord_cartesian(xlim = c(0,NA), ylim = c(0,NA))+
  # theme(axis.title.x = element_blank())+
  xlab(expression("DVM/C Export"))+
  scale_fill_discrete(
    labels = c("5° N","ALOHA S","ALOHA W","Station Papa","N Atlantic"))

```

```{r NPP-relationships-allDepths, dpi=300, fig.width=5, fig.height=3, warning=FALSE}



ggplot(
  data = subset(trophic.mode.mean, Depth > 200),
  aes(x = NPP, y = FWL, color = Location, fill = Location))+
  geom_smooth(
    method = "lm", formula = y ~ poly(x, 2),
    se = TRUE, color = "black", fill="grey", )+
  geom_point(
    size = 3, shape = 21, color = "black")+
  geom_point(
    data = subset(trophic.mode.mean, Depth > 1000),
    size = 3, shape = 1, color = "purple", stroke = 2)+
  theme(axis.title.x = element_blank())+
  ylim(1,2.7) + xlim(0,80) + ylab("Food Web Length")

#### FWL vs NPP ####
noquote("FWL vs NPP")
LM <- lm(
  data = subset(trophic.mode.mean, Depth > 200),
  formula = FWL ~ poly(NPP, degree = 2)
)
summary(LM)
anova(LM)

ggplot(
  data = subset(f.mode.pooled, Depth > 200),
  aes(x = NPP, y = Surface, fill = Location))+
  geom_smooth(
    method = "lm", formula = y ~ poly(x, 2),
    se = TRUE, color = "black", fill="grey", )+
  geom_point(
    size = 3, shape = 21, color = "black")+
  geom_point(
    data = subset(f.mode.pooled, Depth > 1000),
    size = 3, shape = 1, color = "purple", stroke = 2)+
  ylim(0,1) + xlim(0,80) + 
  ylab("f(surface)")+ 
  xlab(expression("NPP (mmol C/"*m^2*"/day)"))+
  scale_y_continuous(
    limits = c(0,1),
    breaks = c(0,0.2,0.4,0.6,0.8,1))

#### f(surface) vs NPP ####
noquote("FWL vs NPP")
LM <- lm(
  data = subset(f.mode.pooled, Depth > 200),
  formula = Surface ~ poly(NPP, degree = 2)
)
summary(LM)
anova(LM)

```

Let's capture the mean values at each site in a table.

```{r NPP-relationships-table}
summary <- 
  cbind(
    aggregate(
      x = cbind(NPP, DVM, Export, Surface) ~ Location,
      data = subset(f.mode.pooled, Depth > 200 & Depth < 1000), 
      FUN = "mean"
    ),
    aggregate(
      x = cbind(FWL, baseTP) ~ Location,
      data = subset(trophic.mode, Depth > 200 & Depth < 1000), 
      FUN = "mean"
    )[-1]
  )
summary <-
  # t(
    cbind(
      summary[1:3],
      round(summary[4:5],2),
      round(summary[6:7],1)
    # )
  )
kable(summary)

```


Depth is the most significant factor affecting contributions from all organic matter sources to the zooplankton food web at any given location. This is intuitive and makes sense. Surface POM becomes less important in general with depth, while sinking POM becomes increasingly important with depth. The nature of the task, then, becomes to figure out what other variable(s) predict the nature of this depth dependence.

```{r summary-depth, dpi = 300, fig.width=8, fig.height=3}
print("===== SURFACE =====")

plot1 <- ggplot(
  data = f.mode.pooled,
  aes(y = Depth, x = Surface, color = Location, fill = Location, shape = Location))+
  geom_smooth(span = 0.5,
    # method = "glm", method.args = list(family = quasibinomial()),
    # method = "lm", formula = y ~ poly(x, 2),
    se = FALSE, alpha = 0.1, orientation = "y")+
  geom_point(
    size = 3, color = "black")+
  scale_shape_manual(values = c(21,22,23,24,21,22),
                     labels = c("5° N","8° N","ALOHA S","ALOHA W","Station Papa","N Atlantic"))+
  scale_y_reverse() + 
  scale_x_continuous(position = "top",
                     breaks = c(0,0.5,1),
                     limits = c(0,1))+
  scale_color_discrete(
    labels = c("5° N","8° N","ALOHA S","ALOHA W","Station Papa","N Atlantic"))+
  scale_fill_discrete(
    labels = c("5° N","8° N","ALOHA S","ALOHA W","Station Papa","N Atlantic"))
  # ggtitle("Surface")

print("===== LARGE =====")
plot2 <- ggplot(
  data = f.mode.pooled,
  aes(y = Depth, x = Large, color = Location, fill = Location, shape = Location))+
  geom_smooth(span = 0.5,
    # method = "glm", method.args = list(family = quasibinomial()),
    # method = "lm", formula = y ~ poly(x, 2),
    se = FALSE, alpha = 0.1, orientation = "y")+
  geom_point(
    size = 3, color = "black")+
  scale_shape_manual(values = c(21,22,23,24,21,22))+
  scale_y_reverse() +
  scale_x_continuous(position = "top",
                     breaks = c(0,0.5,1),
                     limits = c(0,1)) + 
  xlab("Deep Large")
  # ggtitle("Large")

print("===== SMALL =====")
plot3 <- ggplot(
  data = f.mode.pooled,
  aes(y = Depth, x = Small, color = Location, fill = Location, shape = Location))+
  geom_smooth(span = 0.5,
    # method = "glm", method.args = list(family = quasibinomial()),
    # method = "lm", formula = y ~ poly(x, 2),
    se = FALSE, alpha = 0.1, orientation = "y")+
  geom_point(
    size = 3, color = "black")+
  scale_shape_manual(values = c(21,22,23,24,21,22))+
  scale_y_reverse() +
  scale_x_continuous(position = "top",
                     breaks = c(0,0.5,1),
                     limits = c(0,1)) + 
  xlab("Deep Small")
  # ggtitle("Small")

ggarrange(
  plot1, 
  plot2 + theme(axis.title.y = element_blank()), 
  plot3 + theme(axis.title.y = element_blank()),
  nrow = 1, common.legend = TRUE, legend = "right"
)
```

In the euphotic zone, export ratio appears to describe relevant organic matter sources well. Station Papa appears to have an anomalously high export ratio (flux:NPP) compared to other locations in the North Pacific, meaning a given amount of NPP results in greater flux into the mesopelagic zone.

```{r summary-ExportRatio, fig.width=10, fig.asp=0.3, warning=FALSE}

f.mode.pooled$Strata <- factor("EZ", 
                        levels = c("EZ","MPZ upper","MPZ lower","Bathyl"))
f.mode.pooled$Strata[which(f.mode.pooled$Depth > 100)] <- "MPZ upper"
f.mode.pooled$Strata[which(f.mode.pooled$Depth > 700)] <- "MPZ lower"
# f.mode.pooled$Strata[which(f.mode.pooled$Depth > 1000)] <- "Bathyl"
# 
print("===== SURFACE =====")

plot1 <- ggplot(
  data = subset(f.mode.pooled, Strata == "EZ"),
  aes(x = ExportRatio, y = Surface, color = Location, fill = Location, group = Strata))+
  geom_smooth(
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2)+
  geom_point(
    size = 3, shape = 21, color = "black")+
  facet_wrap(~ Strata, nrow = 2)+
  ggtitle("Surface")

print("===== LARGE =====")
plot2 <- ggplot(
  data = subset(f.mode.pooled, Strata == "EZ"),
  aes(x = ExportRatio, y = Large, color = Location, fill = Location, group = Strata))+
  geom_smooth(
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2)+
  geom_point(
    size = 3, shape = 21, color = "black")+
  facet_wrap(~ Strata, nrow = 2)+
  ggtitle("Large")

print("===== SMALL =====")
plot3 <- ggplot(
  data = subset(f.mode.pooled, Strata == "EZ"),
  aes(x = ExportRatio, y = Small, color = Location, fill = Location, group = Strata))+
  geom_smooth(
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2)+
  geom_point(
    size = 3, shape = 21, color = "black")+
  facet_wrap(~ Strata, nrow = 2)+
  ggtitle("Small")

plot4 <- ggplot(
  data = subset(f.mode.pooled, Strata == "EZ"),
  aes(x = NPP, y = Export, color = Location, fill = Location, group = Strata))+
  geom_smooth(method = "lm", se = TRUE, alpha = 0.2)+
  geom_point(
    size = 3, shape = 21, color = "black")+
  coord_cartesian(xlim = c(0,NA), ylim = c(0,NA))+
  ggtitle("C Export vs NPP")

ggarrange(
  plot1, plot2, plot3, plot4,
  nrow = 1, common.legend = TRUE, legend = "bottom"
)
```

```{r summary-NPP, fig.width=8, fig.asp=0.4, warning=FALSE}

f.mode.pooled$Strata <- factor("EZ", 
                        levels = c("EZ","MPZ upper","MPZ lower","Bathyl"))
f.mode.pooled$Strata[which(f.mode.pooled$Depth > 100)] <- "MPZ upper"
f.mode.pooled$Strata[which(f.mode.pooled$Depth > 700)] <- "MPZ lower"
# f.mode.pooled$Strata[which(f.mode.pooled$Depth > 1000)] <- "Bathyl"

print("===== SURFACE =====")

plot1 <- ggplot(
  data = f.mode.pooled,
  aes(x = NPP, y = Surface, color = Location, fill = Location, group = Strata))+
  geom_smooth(
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2)+
  geom_point(
    size = 3, shape = 21, color = "black")+
  facet_wrap(~ Strata, nrow = 1)+
  ggtitle("Surface")
plot1

plot2 <- ggplot(
  data = f.mode.pooled,
  aes(x = NPP, y = Small, color = Location, fill = Location, group = Strata))+
  geom_smooth(
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2)+
  geom_point(
    size = 3, shape = 21, color = "black")+
  facet_wrap(~ Strata, nrow = 1)+
  ggtitle("Small")
plot2
```

Below the euphotic zone, Vertical migrator biomass is the most significant predictor of f(surface), which should absolutely not be surprising.

```{r summary-DVM, fig.width=8, fig.asp=0.4, warning=FALSE}

f.mode.pooled$Strata <- factor("EZ", 
                        levels = c("EZ","MPZ upper","MPZ lower","Bathyl"))
f.mode.pooled$Strata[which(f.mode.pooled$Depth > 100)] <- "MPZ upper"
f.mode.pooled$Strata[which(f.mode.pooled$Depth > 700)] <- "MPZ lower"
# f.mode.pooled$Strata[which(f.mode.pooled$Depth > 1000)] <- "Bathyl"

print("===== SURFACE =====")

plot1 <- ggplot(
  data = f.mode.pooled,
  aes(x = DVM, y = Surface, color = Location, fill = Location, group = Strata))+
  geom_smooth(
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2)+
  geom_point(
    size = 3, shape = 21, color = "black")+
  facet_wrap(~ Strata, nrow = 1)+
  ggtitle("Surface")
plot1

plot2 <- ggplot(
  data = f.mode.pooled,
  aes(x = DVM, y = Small, color = Location, fill = Location, group = Strata))+
  geom_smooth(
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2)+
  geom_point(
    size = 3, shape = 21, color = "black")+
  facet_wrap(~ Strata, nrow = 1)+
  ggtitle("Small")
plot2
```

Let's also check out the proportion of zooplankton doing DVM as a function of NPP.

```{r prop-DVM-vs-NPP, fig.width=5, fig.height=3, warning=FALSE}
#### f(surface) vs NPP ####
noquote("f(surface) vs NPP")
LM <- lm(
  data = subset(f.mode.pooled, Depth > 200),
  formula = Surface ~ poly(NPP, degree = 2)
)
summary(LM)
anova(LM)

ggplot(
  data = subset(f.mode.pooled, Strata == "EZ"),
  aes(x = NPP, y = DVMProp, color = Location, fill = Location, group = Strata))+
  geom_smooth(
    method = "lm", formula = y ~ x,
    se = TRUE, color = "black", fill="grey")+
  geom_point(
    size = 3, shape = 21, color = "black")+
  coord_cartesian(xlim = c(0,NA), ylim = c(0,NA))+
  xlab(expression("NPP (mmol C/"*m^2*"/day)"))+
  xlim(0,80) + ylab("Proportion DVM")

#### proportion DVM vs NPP ####
noquote("proportion DVM vs NPP")
LM <- lm(
  data = subset(f.mode.pooled, Strata == "EZ"),
  formula = DVMProp ~ NPP
)
summary(LM)
anova(LM)
```

Export ratio does pretty well predicting f(large) in the mesopelagic, while NPP does best with f(small) in the MPZ.

```{r summary-ExportRatio-NPP, fig.width=8, fig.asp=0.4, warning=FALSE}

f.mode.pooled$Strata <- factor("EZ", 
                        levels = c("EZ","MPZ upper","MPZ lower","Bathyl"))
f.mode.pooled$Strata[which(f.mode.pooled$Depth > 100)] <- "MPZ upper"
f.mode.pooled$Strata[which(f.mode.pooled$Depth > 700)] <- "MPZ lower"
# f.mode.pooled$Strata[which(f.mode.pooled$Depth > 1000)] <- "Bathyl"

print("===== Surface =====")
plot1 <- ggplot(
  data = f.mode.pooled,
  aes(x = ExportRatio, y = Surface, color = Location, fill = Location, group = Strata))+
  geom_smooth(
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2)+
  geom_point(
    size = 3, shape = 21, color = "black")+
  facet_wrap(~ Strata, nrow = 1)+
  ggtitle("Surface")
plot1

print("===== LARGE =====")
plot2 <- ggplot(
  data = f.mode.pooled,
  aes(x = ExportRatio, y = Large, color = Location, fill = Location, group = Strata))+
  geom_smooth(
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2)+
  geom_point(
    size = 3, shape = 21, color = "black")+
  facet_wrap(~ Strata, nrow = 1)+
  ggtitle("Large")
plot2

print("===== SMALL =====")
plot3 <- ggplot(
  data = f.mode.pooled,
  aes(x = NPP, y = Small, color = Location, fill = Location, group = Strata))+
  geom_smooth(
    method = "glm", method.args = list(family = quasibinomial()),
    se = TRUE, alpha = 0.2)+
  geom_point(
    size = 3, shape = 21, color = "black")+
  facet_wrap(~ Strata, nrow = 1)+
  ggtitle("Small")
plot3
```



# Predictors of DVM biomass? {-}

One interesting question that emerges from this analysis is, to what extent is DVM correlated with other predictors? In other words, do NPP, export or export ratio predict DVM? It's pretty easy to check, so lets fit some quick linear regressions to do this.

```{r predictors-of-DVM, fig.width=8, fig.asp=0.4, warning=FALSE}

plot1 <- ggplot(
  data = data.romero,
  aes(y = migbio.PPZ , x = `NPP (best)`, color = Site, fill = Site))+
  geom_smooth(
    method = "lm", se = TRUE, color = "black", fill = "grey")+
  geom_point(
    size = 3, shape = 21, color = "black")
plot1
MOD1 <- lm(migbio.PPZ ~ `NPP (best)`,
         data = data.romero)
print("----- SUMMARY -----")
summary(MOD1)
print("----- ANOVA -----")
anova(MOD1)


plot1 <- ggplot(
  data = data.romero,
  aes(y = migbio.PPZ , x = fluxC.PPZ.avg, color = Site, fill = Site))+
  geom_smooth(
    method = "lm", se = TRUE, color = "black", fill = "grey")+
  geom_point(
    size = 3, shape = 21, color = "black")
plot1
MOD1 <- lm(migbio.PPZ ~ fluxC.PPZ.avg,
         data = data.romero)
print("----- SUMMARY -----")
summary(MOD1)
print("----- ANOVA -----")
anova(MOD1)

plot1 <- ggplot(
  data = data.romero,
  aes(y = migbio.PPZ , x = fluxC.PPZ.avg/`NPP (best)`, color = Site, fill = Site))+
  geom_smooth(
    method = "lm", se = TRUE, color = "black", fill = "grey")+
  geom_point(
    size = 3, shape = 21, color = "black")
plot1
MOD1 <- lm(migbio.PPZ ~ fluxC.PPZ.avg/`NPP (best)`,
         data = data.romero)
print("----- SUMMARY -----")
summary(MOD1)
print("----- ANOVA -----")
anova(MOD1)

plot1 <- ggplot(
  data = data.romero,
  aes(y = bio.200.day , x = `NPP (best)`, color = Site, fill = Site))+
  geom_smooth(
    method = "lm", se = TRUE, color = "black", fill = "grey")+
  geom_point(
    size = 3, shape = 21, color = "black")
plot1
MOD1 <- lm(bio.200.day ~ `NPP (best)`,
         data = data.romero)
print("----- SUMMARY -----")
summary(MOD1)
print("----- ANOVA -----")
anova(MOD1)

plot1 <- ggplot(
  data = data.romero,
  aes(y = bio.200.day , x = fluxC.PPZ.avg, color = Site, fill = Site))+
  geom_smooth(
    method = "lm", se = TRUE, color = "black", fill = "grey")+
  geom_point(
    size = 3, shape = 21, color = "black")
plot1
MOD1 <- lm(bio.200.day ~ fluxC.PPZ.avg,
         data = data.romero)
print("----- SUMMARY -----")
summary(MOD1)
print("----- ANOVA -----")
anova(MOD1)

```

Looks like NPP is a significant predictor of DVM biomass!